---
title: 'Replication from Amasino et al. (2019)'
output:
  html_document:
    df_print: paged
---

# Setup
```{r, setup, message=FALSE, warning=FALSE}
root = "C:/Users/User/GitHub/WebET_Analysis"
path_results = file.path(root, 'results', 'plots', 'choice_task')

knitr::opts_knit$set(root.dir = normalizePath(file.path('..', '..')))

knitr::opts_knit$get("root.dir")


source(file.path(root, 'utils', 'r', 'geom_split_violin.R'))
source(file.path(root, 'utils', 'r', 'merge_by_index.R'))
source(file.path(root, 'utils', 'r', 'merge_by_subject.R'))
source(file.path(root, 'utils', 'r', 'merge_by_index.R'))
source(file.path(root, 'utils', 'r', 'summarize_datasets.R'))
source(file.path(root, 'utils', 'r', 'get_packages.R'))
source(file.path(root, 'utils', 'r', 'remove_runs.R'))
source(file.path(root, 'utils', 'r', 'add_x_count.R'))
source(file.path(root, 'utils', 'r', 'create_time_bins.R'))
source(file.path(root, 'utils', 'r', 'plot_et_time_bins.R'))
source(file.path(root, 'utils', 'r', 'add_last_fix_top_bottom.R'))
source(file.path(root, 'utils', 'r', 'add_last_fix_ll_amount.R'))

get_packages(c(
	'plyr',
	'dplyr', 
	"effsize",
	'e1071',
	"ggplot2",
	"ggsignif",
	'knitrProgressBar',
	'lme4',
	'progress',
	'QuantPsyc',
	"RColorBrewer",
	'reshape2',
	'tidyr'))

print(getwd())
```


# Read and create datasets
```{r, load_datasets}
path=file.path(root, 'data', 'choice_task', 'cleaned')
data_subject = read.csv(file.path(path, 'data_subject.csv'))
data_trial = read.csv(file.path(path, 'data_trial.csv'))
data_et = read.csv(file.path(path, 'data_et.csv'))

summarize_datasets(data_et, data_trial, data_subject)
```

## add_k-values
```{r, add_k_values}
data_trial = merge_mean_by_subject(data_trial, data_subject, 'logK')
data_trial = merge_mean_by_subject(data_trial, data_subject, 'noise')
```


## fixations
```{r, add_fixations}
grouped_fixations = data_et %>%
    group_by(run_id, withinTaskIndex) %>%
    dplyr::summarise(
        n_fixations = length(unique(fix_counter)),
        .groups='keep')

data_trial = merge(
    data_trial,
    grouped_fixations,
    by=c('run_id', 'withinTaskIndex'))

summary(data_trial$n_fixations)
```


# Distribution of add_k-values
````{r, plot_k}
dir.create(file.path(path_results, 'log_k'), showWarnings = FALSE)

ggplot(data_subject, aes(x=logK))+
    geom_histogram(binwidth=.5, alpha=.5, position="identity")+
    scale_fill_manual(values=c("palegreen","cornflowerblue"), name="") +
    theme_bw()+theme(text=element_text(size=40))
ggsave(file.path(path_results, 'log_k', 'log_k_histogram.png'), 
	   width=5.5, height=5)

ggplot(data_subject, aes(x=noise))+
    geom_histogram(binwidth=1, alpha=.5, position="identity")+
    scale_fill_manual(values=c("palegreen","cornflowerblue"), name="") +
    theme_bw()+theme(text=element_text(size=40))
ggsave(file.path(path_results, 'log_k', 'noise_histogram.png'), 
	   width=5.5, height=5)

ggplot(data_subject, aes(x=logK, y=noise)) +
    geom_point(size=2.5, aes(alpha=.5))+
    guides(alpha=FALSE,color=FALSE, shape=FALSE)+
    theme_bw() + 
    scale_colour_grey() + 
    theme(text=element_text(size=20)) +
    xlab("logK") + ylab("noise") +
    ggtitle('logK vs. noise') 
ggsave(file.path(path_results, 'log_k', 'log_k_vs_noise.png'), 
	   width=5.5, height=5)
````


# Histogram of left/right and top/bottom choice distribution
```{r, plot_prop_top}
sd(data_subject$choseTop)


dir.create(file.path(path_results, 'behavior'),  showWarnings = FALSE)
ggplot(data_subject, aes(x=choseTop)) +
	geom_histogram(bins=15) + 
	xlab("Proportion Top Choices") +
	theme_bw() + 
	theme(text=element_text(size=20))+xlim(0,1)

ggsave(file.path(path_results, 'behavior', 'top_vs_bottom_choices.png'), 
	   width=5.5, height=5)
```


# Subjective value 
## Subjective value for top and bottom options
```{r}
subjectiveValues = function(data) {
    data$svLL = data$aLL / (1 + exp(data$logK) * data$tLL)
    data$svSS = data$aSS / (1 + exp(data$logK) * data$tSS)
    data$dSV_LLSS = data$svLL - data$svSS
    
    data$svT = data$aT / (1+ exp(data$logK) * data$tT)
    data$svB = data$aB / (1+ exp(data$logK) * data$tB)
    data$dSV_TB = data$svT - data$svB
    
    return(data)
}

data_trial = subjectiveValues(data_trial)


data_trial %>%
    dplyr::select(run_id, aT, tT, svT, aB, tB, svB, dSV_TB, choseTop) %>%
    mutate(across(c('svT', 'svB', 'dSV_TB'), round, 2)) %>%
    arrange(dSV_TB) %>%
	head(5)
```

## ChoseTop by dSV bins
```{r}
data_trial$dSV_bin = cut(
				data_trial$dSV_TB,
		    breaks = seq(-5, 5, 1),
		    labels = seq(-4.5, 4.5, 1),
    include.lowest=TRUE) %>%
    paste() %>%
    as.numeric()

SV_bins = data_trial %>%
		add_x_count(data_et) %>%
    dplyr::group_by(run_id, dSV_bin) %>%
    dplyr::summarise(
        n=n(),
        logK = mean(logK),
        noise = mean(noise),
        choseTop=mean(choseTop), 
        rt=mean(trial_duration_exact)/1000, 
        n_fixations = mean(n_fixations),
        count=mean(x_count),
        .groups = 'keep') %>%
    filter(n>1) %>%
    arrange(dSV_bin)

SV_bins %>% head(5)

print(paste(
    'Remaining subjects: ', 
    SV_bins %>% 
        dplyr::pull(run_id) %>%
        unique() %>%
        length()))

dir.create(file.path(path_results, 'SV'),  showWarnings = FALSE)

ggplot(data=SV_bins, aes(x=dSV_bin, y=choseTop)) + 
    theme_bw() +
    geom_line(color='grey',alpha=.2, aes(group=as.numeric(run_id))) +
    xlim(-5,5) +
    geom_line(stat="summary", fun="mean", size=.5)+
    stat_summary(fun.data=mean_se, geom="errorbar", width=.8)+
    xlab("SV top - SV bottom")+ylab("Proportion top choices")+
    theme(text=element_text(size=20))+ylim(0,1)
ggsave(file.path(path_results, 'SV', 'choseTop.png'), 
	   width=5.5, height=5)

ggplot(data=SV_bins, aes(x=dSV_bin, y=rt)) +
    theme_bw() +
    geom_line(color='grey',alpha=.2, aes(group=as.numeric(run_id))) +
    xlim(-5,5) + ylim(0, 6.5) +
    geom_line(stat="summary", fun="mean", size=.5) +
    stat_summary(fun.data=mean_se, geom="errorbar", width=.8) +
    xlab("SV top - SV bottom") + 
    ylab("Response Time (s)") +
    theme(text=element_text(size=20))
ggsave(file.path(path_results, 'SV', 'rt.png'),width=5.5, height=5)

ggplot(data=SV_bins, aes(x=dSV_bin, y=n_fixations)) +
    theme_bw() +
    geom_line(color='grey',alpha=.2, aes(group=as.numeric(run_id))) +
    xlim(-5,5) + ylim(0,15) + 
    geom_line(stat="summary", fun="mean", size=.5) +
    stat_summary(fun.data=mean_se, geom="errorbar", width=.8) +
    xlab("SV top - SV bottom") + 
    ylab("Number of Fixations") +
    theme(text=element_text(size=20))
ggsave(file.path(path_results, 'SV', 'fixations.png'),width=5.5, height=5)
```

# Eye tracking indices
## Correlation of Eye tracking indices and discount rate
```{r, eyetracking_indices}
dir.create(file.path(path_results, 'et'),  showWarnings = FALSE)
ggplot(data_subject %>% filter(!is.na(optionIndex)), 
       aes(x=optionIndex, y=logK)) +
		geom_point(size=2.5, aes(alpha=.5)) +
		guides(alpha=FALSE,color=FALSE, shape=FALSE) +
		theme_bw() + 
		xlim(-1,1) +
		theme(text=element_text(size=20))+
		xlab("Option index") +
		ylab("log(add_k)") +
		scale_colour_grey()
ggsave(file.path(path_results, 'et', 'logK_oi.png'), width=5.7, height=5)

data_test = data_subject %>% filter(!is.na(optionIndex))
cor.test(data_test$optionIndex, data_test$logK) 

ggplot(data_subject %>% filter(!is.na(attributeIndex)), 
       aes(x=attributeIndex, y=logK)) +
		geom_point(size=2.5, aes(alpha=.5)) +
		guides(alpha=FALSE,color=FALSE, shape=FALSE) +
		theme_bw() + 
		xlim(-1,1) +
		scale_colour_grey()
		theme(text=element_text(size=20)) +
		xlab("Attribute index") + ylab("log(add_k)")
ggsave(file.path(path_results, 'et', 'logK_ai.png'),width=5.7, height=5)

data_test = data_subject %>% filter(!is.na(attributeIndex))
cor.test(data_test$attributeIndex, data_test$logK) 

#Plot correlation between Payne index and discount rate
#Replication sample
ggplot(data_subject %>% filter(!is.na(attributeIndex)), 
       aes(x=payneIndex, y=logK)) +
		geom_point(size=2.5, aes(alpha=.5))+
		guides(alpha=FALSE,color=FALSE, shape=FALSE)+
		theme_bw() + 
		xlim(-1,1) + 
		scale_colour_grey() + 
		theme(text=element_text(size=20))+
		xlab("Payne index") +
		ylab("log(add_k)")
ggsave(file.path(path_results, 'et', 'logK_pi.png'),width=5.7, height=5)

data_test = data_subject %>% filter(!is.na(payneIndex))
cor.test(data_test$payneIndex, data_test$logK) 
```

## Correlation of Eye tracking indices among each other
```{r}
ggplot(data_subject %>% 
           filter(!is.na(optionIndex) & !is.na(attributeIndex)), 
       aes(x=optionIndex, y=attributeIndex)) +
		geom_point(size=2.5, aes(alpha=.5)) +
		guides(alpha=FALSE,color=FALSE, shape=FALSE) +
		theme_bw() + 
		xlim(-1,1) +
		theme(text=element_text(size=20))+
		xlab("Option index") +
		ylab("Attribute Index") + 
		scale_colour_grey()
ggsave(file.path(path_results, 'et', 'oi_ai.png'),width=5.7, height=5)

data_test = data_subject %>% 
    filter(!is.na(optionIndex) & !is.na(attributeIndex))
cor.test(data_test$optionIndex, data_test$attributeIndex) 

ggplot(data_subject %>% 
           filter(!is.na(optionIndex) & !is.na(payneIndex)), 
       aes(x=optionIndex, y=payneIndex)) +
		geom_point(size=2.5, aes(alpha=.5))+
		guides(alpha=FALSE,color=FALSE, shape=FALSE) +
		theme_bw() + 
		xlim(-1,1) +
		scale_colour_grey()
		theme(text=element_text(size=20)) +
		xlab("Option Index") + ylab("Payne Index") 
ggsave(file.path(path_results, 'et', 'oi_pi.png'), width=5.7, height=5)

data_test = data_subject %>% 
    filter(!is.na(optionIndex) & !is.na(payneIndex))
cor.test(data_test$optionIndex, data_test$payneIndex) 

#Plot correlation between Payne index and discount rate
#Replication sample
ggplot(data_subject %>% 
    filter(!is.na(payneIndex) & !is.na(attributeIndex)), 
       aes(x=attributeIndex, y=payneIndex)) +
		geom_point(size=2.5, aes(alpha=.5))+
		guides(alpha=FALSE,color=FALSE, shape=FALSE) +
		theme_bw() + 
		xlim(-1,1) + 
		scale_colour_grey() + 
		theme(text=element_text(size=20)) +
		xlab("Attribute index") +
		ylab("Payne Index") 
ggsave(file.path(path_results, 'et', 'ai_pi.png'), width=5.7, height=5)

data_test = data_subject %>% 
    filter(!is.na(payneIndex) & !is.na(attributeIndex))
cor.test(data_test$attributeIndex, data_test$payneIndex) 
```

### Trial bins
Little variance across the trials but this could also be due to the lower sample size
```{r}
data = data_trial
nBins = 8

data = data %>%
    mutate(trial_bin = cut(
    		withinTaskIndex, nBins, include.lowest=TRUE, labels=c(1:nBins)))
    
grouped_choseLL = data %>% 
    group_by(run_id, trial_bin) %>%
    dplyr::summarise(
    	choseLL = mean(choseLL),
    	.groups='keep')

grouped_trialMeans = data %>%
    group_by(trial_bin) %>%
    dplyr::summarise(
    	trialMeans = mean(withinTaskIndex),
    	.groups = 'keep')

trial_bins = merge(grouped_choseLL, grouped_trialMeans, by='trial_bin')

trial_bins %>% head(5)

ggplot(
    data=trial_bins, 
    aes(x=trialMeans, y=choseLL)) + 
    theme_bw() +
    geom_line(color='grey',alpha=.2, aes(group=as.numeric(run_id))) +
    xlim(0, 80) +
    geom_line(stat="summary", fun="mean", size=.5)+
    stat_summary(fun.data=mean_se, geom="errorbar", width=.8)+
    xlab("Trial_index") + 
    ylab("Proportion LL choices") + 
    ggtitle("ChoseLL across trials") +
    theme(text=element_text(size=20))+ylim(0,1)
ggsave(file.path(path_results, 'behavior', 'chose_ll_vs_trials.png'), 
			 width=5.7, height=5)
```




# Eye Tracking Bins
Eye tracking bins with average proportion of looking top for each 
subject over trials when they chose the top option or the bottom option.

## Create time bins
```{r}
data_et = create_time_bins(data_et, 5)

data_et %>%
    dplyr::select(run_id, withinTaskIndex, time_bin, t_task, aoi) %>%
    arrange(run_id, withinTaskIndex, time_bin, t_task) %>% 
	head(5)
```


```{r}
data_time_bins =  data_et %>%
	merge_by_index(data_trial, 'choseTop') %>%
    filter(!is.na(aoi) & !aoi %in% c(0, '0')) %>%
    mutate(
        lookTop = as.numeric(aoi %in% c('TL', 'TR')), 
        lookBottom = as.numeric(aoi %in% c('BL', 'BR'))) %>%
    dplyr::group_by(run_id, choseTop, time_bin) %>%
    dplyr::summarise(
        n_trials = n(),
        n_lookTop = sum(lookTop),
        n_lookBottom = sum(lookBottom),    
        p_lookTop = sum(lookTop)/n_trials,
        p_lookBottom = sum(lookBottom)/n_trials,
        .groups = 'keep') %>%
	mutate(
		choseTop = factor(choseTop, c('1', '0')), 
		time_bin = factor(time_bin)) %>%
	merge_by_subject(data_subject, 'window') %>%
	merge_by_subject(data_subject, 'fps') %>%
	dplyr::select(
		run_id, window, fps, choseTop, time_bin, n_trials, 
		n_lookTop, n_lookBottom, p_lookTop, p_lookBottom)

for (bin in unique(time_bins_choseTB_long$time_bin)) {
    print(t.test(p_lookTop ~ choseTop, 
                 data=time_bins_choseTB_long %>% 
                     filter(time_bin==bin &
                            !(run_id %in% subjects_not_enough_bins)), 
                 paired=TRUE))
}

plot_et_time_bins(time_bins_choseTB_long)
ggsave(file.path(path_results, 'et', 'bins_top_vs_bottom.png'), 
			 width=5.5, height=5)
```

# Last fixation
## Proportion of top choice 
```{r}
data_trial = add_last_fix_top_bottom(data_trial, data_et)

data_trial %>%
    dplyr::select(run_id, trial_index, choseTop, last_fix_top) %>% 
	head(5)
```

```{r}
lastGaze_long <- data_trial %>%
    dplyr::select(run_id, withinTaskIndex, last_fix_top, choseTop) %>%
    dplyr::group_by(run_id, last_fix_top, withinTaskIndex) %>%
    dplyr::summarise(
    	choseTop=mean(choseTop),
    	.groups = 'keep') %>%
    dplyr::group_by(run_id, last_fix_top) %>%
    dplyr::summarise(
        n=n(),
    	choseTop=mean(choseTop),
        .groups = 'keep') 

lastGaze_long %>% head(5)

# t-test
subjects_noGaze = 
    lastGaze_long %>% 
    group_by(run_id) %>%
    dplyr::summarise(n_subj = n()) %>%
    filter(n_subj<2) %>%
    arrange(run_id) %>%
    dplyr::pull(run_id)

lastGaze_long$last_fix_top = factor(lastGaze_long$last_fix_top, c('1', '0'))
t.test(
    choseTop ~ last_fix_top,
    data=lastGaze_long %>% filter(!(run_id %in% subjects_noGaze)), 
    paired=TRUE)

# plot
ggplot(lastGaze_long, aes(x=last_fix_top, y=choseTop)) +
    geom_violin(fill="gray", size=0) +
    stat_summary(fun=mean,geom="point",shape=45,size=10, color="white") +
    geom_text(x=1.5, y=1.02, label="***") + 
    annotate("segment",x=1, xend=2, y=1.01, yend=1.01) +
    theme_bw()+ylim(0,1.03)+xlab("") + 
    ylab("Proportion top choices") +
    xlab("last Fixation on Top AOIs") + 
    theme(text=element_text(size=20))
ggsave(file.path(path_results, 'et', 'last_gaze_vs_choice.png'), 
			 width=5.5, height=5)
```


## Proportion of LL choice 
```{r}
add_lastGazeLL = function(data_trial, data_et) {
    grouped_lastCoordinate = data_et %>%
        dplyr::group_by(run_id, trial_index) %>%
        dplyr::summarise(
        	t_task = max(t_task), 
        	.groups = 'keep') %>%
        merge(data_et %>% 
                  dplyr::select(run_id, trial_index, t_task, aoi, LL_top) %>%
                  filter(aoi!="0"), 
              by=c('run_id', 'trial_index', 't_task')) %>%
        mutate(lastGazeLL = as.numeric(
            (aoi %in% c('TL', 'TR') & LL_top==1) |
            (aoi %in% c('BL', 'BR') & LL_top==0)), 
        ) 
   
    if ('lastGazeLL' %in% names(data_trial)) {
        data_trial = data_trial %>% dplyr::select(!lastGazeLL)}
    data_trial = data_trial %>% 
        merge(
            grouped_lastCoordinate %>% 
                dplyr::select(run_id, trial_index, lastGazeLL), 
            by=c('run_id', 'trial_index'))
    
    return(data_trial)
}

data_trial = add_lastGazeLL(data_trial, data_et)
```

```{r}
grouped_lastCoordinate = data_et %>%
    dplyr::group_by(run_id, trial_index) %>%
    dplyr::summarise(
    	t_task = max(t_task), 
    	.groups='keep') %>%
    merge(data_et %>% 
              dplyr::select(run_id, trial_index, t_task, aoi, LL_top) %>%
              filter(aoi!="0"), 
          by=c('run_id', 'trial_index', 't_task')) %>%
    mutate(lastGazeLL = as.numeric(
        (aoi %in% c('TL', 'TR') & LL_top==1) |
        (aoi %in% c('BL', 'BR') & LL_top==0)), 
    ) %>% 
    merge(data_trial %>%
              dplyr::select(run_id, trial_index, 
                            option_TL, option_TR, option_BR, option_BL,
                            choseLL),
          by=c('run_id', 'trial_index'))

grouped_lastCoordinate %>%
    filter(lastGazeLL==0) %>% 
	head(5)
```

```{r}
lastGaze_long <- data_trial %>% 
    dplyr::select(run_id, withinTaskIndex, lastGazeLL, choseLL) %>%
    dplyr::group_by(run_id, lastGazeLL, withinTaskIndex) %>%
    dplyr::summarise(
    	choseLL=mean(choseLL),
    	.groups = 'keep') %>%
    dplyr::group_by(run_id, lastGazeLL) %>%
    dplyr::summarise(
        n = n(),
        choseLL = mean(choseLL),
        .groups = 'keep') 

lastGaze_long %>% head(5)

subjects_noGaze = lastGaze_long %>% 
    group_by(run_id) %>%
    dplyr::summarise(
    	n_subj = n(), 
    	.groups = 'keep') %>%
    filter(n_subj<2) %>%
    arrange(run_id) %>%
    dplyr::pull(run_id)

lastGaze_long$lastGazeLL = factor(lastGaze_long$lastGazeLL, c('1', '0'))
t.test(
    choseLL ~ lastGazeLL,
    data=lastGaze_long %>% filter(!(run_id %in% subjects_noGaze)), 
    paired=TRUE)

ggplot(lastGaze_long, 
       aes(x=lastGazeLL, y=choseLL)) +
    geom_violin(fill="gray", size=0) +
    stat_summary(fun=mean,geom="point",shape=45,size=10, color="white") +
    geom_text(x=1.5, y=1.02, label="***") + 
    annotate("segment",x=1, xend=2, y=1.01, yend=1.01) +
    theme_bw()+ylim(0,1.03)+xlab("") + 
    ylab("Proportion LL choices") +
    xlab("last Fixation on LL AOIs") + 
    theme(text=element_text(size=20))
ggsave(file.path(path_results, 'et', 'last_fix_ll_vs_choice_ll.png'), 
			 width=5.5, height=5)
```



# Error Analyis
Error trials are those that are not predicted based on the subjective values, 
which themselves are based on individual's fitted add_k value

## Filter for missing logK
```{r}
data_trial = data_trial %>% 
	filter(!is.na(logK))

data_subject = data_subject %>% 
	filter(!is.na(logK))
```

## Find Error trials
```{r}
identify_error_trials = function(data) {
    data$predictLL = as.integer(data$svLL > data$svSS)
    data$errorTrial = as.integer((data$choseLL != data$predictLL))
    data$patientError = as.integer((data$choseLL & !data$predictLL))
    data$impatientError = as.integer((!data$choseLL & data$predictLL))
    return(data)
}

data_trial = identify_error_trials(data_trial)

data_trial %>% 
    dplyr::select(svLL, svSS, predictLL, choseLL, 
                  errorTrial, patientError, impatientError) %>% 
	head(5)
   
data_trial %>%
    dplyr::group_by(run_id) %>%
    dplyr::summarise(
    	choseLL = mean(choseLL), 
    	errorTrial=sum(errorTrial),
    	.groups = 'keep') %>% 
	head(5)
```


## Find Correct trial for each Error trial
````{r}
matchTrials = function(data) {
    data$matched_trial=0
    for (i in 1:nrow(data)) {
        if (data[i, ]$errorTrial) {
            if (data[i, ]$impatientError) {
                correctTrials = data %>% 
                    filter(
                        run_id==data[i, ]$run_id & 
                        !errorTrial & choseLL) %>%
                    dplyr::select(run_id, withinTaskIndex, dSV_LLSS)
                
            } 
            if (data[i, ]$patientError) {
                correctTrials = data %>% 
                    filter(
                        run_id==data[i, ]$run_id & 
                        !errorTrial & !choseLL) %>%
                    dplyr::select(run_id, withinTaskIndex, dSV_LLSS)
            }
        # If it is an error trial  
            
            if (nrow(correctTrials) > 0) {
                correctTrials$dSV_difference = 
                    abs(correctTrials$dSV_LLSS - data[i, ]$dSV_LLSS)
            
                matched_trials = correctTrials %>%
                    filter(dSV_difference == 
                                min(correctTrials$dSV_difference)) %>%
                    dplyr::pull(withinTaskIndex)
            
                data[i, ]$matched_trial = matched_trials[1]
                
                if (length(matched_trials)>1) {
                    already_matched = data %>% 
                        filter(run_id==data[i, ]$run_id) %>%
                        dplyr::pull(matched_trial)
                  
                    for (j in 1:length(matched_trials)) {
                        if (!(matched_trials[j] %in% already_matched)) {
                            data[i, ]$matched_trial = matched_trials[j]
                        }
                    }
                }
            }
        }
    }
    return(data)
}

data_trial = matchTrials(data_trial)

data_trial %>% 
#    filter(errorTrial==1) %>%
    dplyr::select(errorTrial, patientError, 
    			  impatientError, matched_trial) %>% 
	head(5)

````

## ET indices and reaction time for error trials
Do subjects behave differently when they correctly choose LL (as expected) than when they unexpectedly chose SS instead?

### Group by LL or SS expected
```{r}
data_trial = data_trial %>%
    mutate(LLexpected = as.numeric(svLL > svSS))

data_trial %>%
    dplyr:: select(svLL, svSS, LLexpected) %>% 
	head(5)
```


### Filter those subjects with matched error and correct trials
````{r}
subjects_LLcorrect = data_trial %>%
    filter(LLexpected==1) %>%
    dplyr::group_by(run_id) %>%
    dplyr::summarise(
    	n_unique_matched = length(unique(matched_trial)),
    	.groups = 'keep') %>%
    filter(n_unique_matched>2) %>%
    dplyr::pull(run_id)
subjects_LLcorrect

length(subjects_LLcorrect)

subjects_SScorrect = data_trial %>%
    filter(LLexpected==0) %>%
    dplyr::group_by(run_id) %>%
    dplyr::summarise(
    	n_unique_matched = length(unique(matched_trial)),
    	.groups = 'keep') %>%
    filter(n_unique_matched>2) %>%
    dplyr::pull(run_id)
subjects_SScorrect

length(subjects_SScorrect)
```


Dianna found differences reaction time and option index

### group_by(LLexpected, run_id, errorTrial)
```{r}
grouped = data_trial %>%
    filter(
        (LLexpected==1 & run_id %in% subjects_LLcorrect) |
        (LLexpected==0 & run_id %in% subjects_SScorrect)) %>%
    dplyr::group_by(LLexpected, run_id, errorTrial) %>%
    dplyr::summarise(
    	n = n(), 
		rt = mean(trial_duration_exact), 
		optionIndex = mean(optionIndex), 
		attributeIndex = mean(attributeIndex),
		payneIndex = mean(payneIndex),
		.groups = 'keep') %>%
    mutate(
        errorTrial = factor(errorTrial),
        rt = rt/1000)

grouped %>% head(5)
```

## t-test LL expected 
Do subjects behave differently when they correctly choose LL (as expected) than when they unexpectedly chose SS instead?
`````{r}
runs_na_oi = data_subject %>%
	filter(is.na(optionIndex)) %>%
	dplyr::pull(run_id)

runs_na_ai = data_subject %>%
	filter(is.na(attributeIndex)) %>%
	dplyr::pull(run_id)

runs_na_pi = data_subject %>%
	filter(is.na(payneIndex)) %>%
	dplyr::pull(run_id)
	

t.test(rt ~ errorTrial,
       data=grouped %>% filter(
           LLexpected==1),
       paired=TRUE, na.action=na.omit)

cohen.d(rt ~ errorTrial,alpha=.05,
		data=grouped %>% filter(LLexpected==1))

runs_na_error_oi = grouped %>% filter(
		   	!is.na(optionIndex) &
		   	LLexpected==1 & 
	   		!run_id %in% c(runs_na_oi)) %>%
	group_by(run_id) %>%
	dplyr::summarise(
		n=n(),
		.groups='keep') %>%
	filter(n<2) %>%
	dplyr::pull(run_id)

t.test(optionIndex ~ errorTrial,
       data=grouped %>% filter(
		   	!is.na(optionIndex) &
		   	LLexpected==1 & 
	   		!run_id %in% c(runs_na_oi, runs_na_error_oi)),
       paired=TRUE, na.action=na.omit)

runs_na_error_ai = grouped %>% 
	filter(!is.na(attributeIndex) &
   	   	   LLexpected==1 & 
   		   !run_id %in% c(runs_na_ai)) %>%
	group_by(run_id) %>%
	dplyr::summarise(
		n=n(),
		.groups='keep') %>%
	filter(n<2) %>%
	dplyr::pull(run_id)

t.test(attributeIndex ~ errorTrial,
       data=grouped %>% filter(
           LLexpected==1 & !run_id %in% c(runs_na_ai, runs_na_error_ai)),
       paired=TRUE, na.action=na.omit)

runs_na_error_pi = grouped %>% 
	filter(!is.na(payneIndex) &
		 	LLexpected==1 & 
      		!run_id %in% c(runs_na_pi)) %>%
	group_by(run_id) %>%
	dplyr::summarise(
		n=n(),
		.groups='keep') %>%
	filter(n<2) %>%
	dplyr::pull(run_id)
# 
# t.test(payneIndex ~ errorTrial,
#        data=grouped %>% filter(
#            LLexpected==1 & !run_id %in% c(runs_na_pi, runs_na_error_pi)),
#        paired=TRUE, na.action=na.omit)
````


## SS expected 
Do subjects behave differently when they correctly choose SS (as expected) than when they unexpectedly chose LL instead?
````{r}
runs_na_oi = data_subject %>%
	filter(is.na(optionIndex)) %>%
	dplyr::pull(run_id)

runs_na_ai = data_subject %>%
	filter(is.na(attributeIndex)) %>%
	dplyr::pull(run_id)

runs_na_pi = data_subject %>%
	filter(is.na(payneIndex)) %>%
	dplyr::pull(run_id)


t.test(rt ~ errorTrial,
       data=grouped %>% filter(
           LLexpected==0),
       paired=TRUE, na.action=na.omit)

runs_na_error_oi = grouped %>% filter(
		   	!is.na(optionIndex) &
		   	LLexpected==0 & 
	   		!run_id %in% c(runs_na_oi)) %>%
	group_by(run_id) %>%
	dplyr::summarise(
		n=n(),
		.groups='keep') %>%
	filter(n<2) %>%
	dplyr::pull(run_id)

t.test(optionIndex ~ errorTrial,
       data=grouped %>% filter(
		   	!is.na(optionIndex) &
		   	LLexpected==0 & 
	   		!run_id %in% c(runs_na_oi, runs_na_error_oi)),
       paired=TRUE, na.action=na.omit)

runs_na_error_ai = grouped %>% 
	filter(!is.na(attributeIndex) &
   	   	   LLexpected==0 & 
   		   !run_id %in% c(runs_na_ai)) %>%
	group_by(run_id) %>%
	dplyr::summarise(
		n=n(),
		.groups='keep') %>%
	filter(n<2) %>%
	dplyr::pull(run_id)

t.test(attributeIndex ~ errorTrial,
       data=grouped %>% filter(
           LLexpected==0 & !run_id %in% c(runs_na_ai, runs_na_error_ai)),
       paired=TRUE, na.action=na.omit)

runs_na_error_pi = grouped %>% 
	filter(!is.na(payneIndex) &
		 	LLexpected==0 & 
      		!run_id %in% c(runs_na_pi)) %>%
	group_by(run_id) %>%
	dplyr::summarise(
		n=n(),
		.groups='keep') %>%
	filter(n<2) %>%
	dplyr::pull(run_id)

# t.test(payneIndex ~ errorTrial,
#        data=grouped %>% filter(
#            LLexpected==0 & !run_id %in% c(runs_na_pi, runs_na_error_pi)),
#        paired=TRUE, na.action=na.omit)
```


```{r, message=FALSE, warning=FALSE}
data_plot = grouped %>%
    mutate(
        errorTrial = mapvalues(
            factor(errorTrial), 
            from = c(0, 1), 
            to = c("Correct", "Error")),
        LLexpected = factor(LLexpected))

ggplot(data_plot, aes(x=LLexpected, y=rt, fill=errorTrial)) +
  geom_violin(alpha=.6, size=0, position=position_dodge(0)) +
  stat_summary(
      fun.data="mean_se",
      geom="linerange",
      aes(color=errorTrial),
      alpha=1,
      size=1.5) +
  stat_summary(
      fun=mean, 
      geom="line",
      aes(group=errorTrial, color=errorTrial), 
      size=1.5) +
  # geom_text(x=2, y=7.4, label="***",size=10) + 
  coord_cartesian(ylim=c(0,7.5)) +
  theme_bw() + 
  theme(text=element_text(size=20),
  	    legend.position="bottom") +
  scale_x_discrete(labels=c("SS>LL", "LL>SS")) +
  xlab("Choices") + ylab("Response Time (s)") + 
  labs(fill="",color="")+
  guides(size="none") + 
  scale_colour_grey() + scale_fill_grey()
ggsave(file.path(path_results, 'behavior', 'error_trials_vs_rt.png'), 
			 width=5.5, height=5)
```

```{r}
ggplot(
    data_plot %>% filter(
        !is.na(optionIndex)), 
       aes(x=LLexpected, y=optionIndex, fill=errorTrial)) +
  geom_split_violin(alpha=.6, size=0, position=position_dodge(0)) +
  stat_summary(
      fun.data="mean_se",
      geom="linerange",
      aes(color=errorTrial),
      alpha=1,
      size=1.5) +
  stat_summary(
      fun=mean, 
      geom="line",
      aes(group=errorTrial, color=errorTrial), 
      size=1.5) +
  # geom_text(x=2, y=7.4, label="***",size=10) + 
  coord_cartesian(ylim=c(-2.5, 2.5)) +
  theme_bw() + 
  theme(text=element_text(size=20)) +
  scale_x_discrete(labels=c("SS>LL", "LL>SS")) +
  xlab("Choices") + ylab("Option Index") + 
  labs(fill="",color="")+
  guides(size="none") + 
  scale_colour_grey() + scale_fill_grey()
ggsave(file.path(path_results, 'et', 'error_trials_vs_oi.png'), 
			 width=5.5, height=5)
```