---
title: 'Analyzing eye-tracking behavior vs. choices'
output:
  html_document:
    df_print: paged
---

# Setup
```{r, setup, message=FALSE, warning=FALSE}
root = "C:/Users/User/GitHub/WebET_Analysis"

path_results = file.path(root, 'results', 'plots', 'choice_task')
# Create directory for plots
dir.create(file.path(path_results, 'et', 'time_bins'),
		   showWarnings = FALSE)

knitr::opts_knit$set(root.dir = normalizePath(file.path('..', '..')))

knitr::opts_knit$get("root.dir")


source(file.path(root, 'utils', 'r', 'geom_split_violin.R'))
source(file.path(root, 'utils', 'r', 'merge_by_subject.R'))
source(file.path(root, 'utils', 'r', 'merge_mean_by_subject.R'))
source(file.path(root, 'utils', 'r', 'merge_by_index.R'))
source(file.path(root, 'utils', 'r', 'summarize_datasets.R'))
source(file.path(root, 'utils', 'r', 'get_packages.R'))
source(file.path(root, 'utils', 'r', 'remove_runs.R'))
source(file.path(root, 'utils', 'r', 'add_x_count.R'))
source(file.path(root, 'utils', 'r', 'add_new_aoi.R'))

get_packages(c(
	'plyr',
	'dplyr', 
	"effsize",
	'e1071',
	"ggplot2",
	"ggsignif",
	'knitrProgressBar',
	'lme4',
	'progress',
	'QuantPsyc',
	"RColorBrewer",
	'reshape2',
	'tidyr'))

print(getwd())
```

# Specific participants
```{r}
choice_best_runs = c(7, 45, 48, 58, 63, 96, 103, 197, 212, 238, 344, 358, 
					 376, 454)

fix_best_runs = c(16,41,126,162,199,205,253,299,318,347,378,414,418,420,427,
				  437,491)

clustering_best_runs = c(7,32,45,48,63,96,126,128,130,197,205,212,238,275,
						 280,288,344,420)
```


# Prep data 
## Load data
```{r, load_datasets}
data_subject = read.csv(
    file.path(root, 'data', 'choice_task', 'cleaned', 
              'data_subject.csv'))

data_trial = read.csv(
    file.path(root, 'data', 'choice_task', 'cleaned', 
              'data_trial.csv'))

data_et = read.csv(
    file.path(root, 'data', 'choice_task', 'cleaned', 
              'data_et.csv'))

summarize_datasets(data_et, data_trial, data_subject)
```

## Check AOI (optionally new AOIs)
```{r}
# data_et = add_new_aoi(data_et, 0.40, 0.40)

ggplot(data_et %>% filter(aoi != 0), aes(x=x, y=y)) +
    geom_point(size=2.5, aes(alpha=.5))+
    guides(alpha=FALSE,color=FALSE, shape=FALSE)+
    theme_bw() + 
	xlim(0, 1) + ylim(1, 0) +
    scale_colour_grey() + 
    theme(text=element_text(size=20)) +
    xlab("x") + ylab("y") +
    ggtitle('AOIs') 
```

## Window
```{r}
grouped_window = data_trial %>%
	mutate(window_diagonal = sqrt(
		window_width * window_width + 
		window_height * window_height)) %>%
	group_by(run_id) %>%
	dplyr::summarise(
		window = max(window_diagonal),
		.groups = 'keep')
data_subject = merge_by_subject(data_subject, grouped_window, 'window')
```



# Gaze points ~ choice
```{r}
grouped = data_et %>% 
	merge_by_index(data_trial, 'choseTop') %>%
	merge_by_index(data_trial, 'choseLL') %>%
	merge_by_index(data_trial, 'LL_top') %>%
	filter(!is.na(aoi) & !aoi %in% c(0, '0')) %>%
	dplyr::group_by(run_id, trial_index) %>%
	dplyr::summarise(
		n = n(),
		n_bottom = sum(aoi %in% c('BL', 'BR')), 
		p_look_bottom = n_bottom / n,
		choseTop = mean(choseTop), 
		n_SS = sum(
			(LL_top==1 & aoi %in% c('BL', 'BR')) |
			(LL_top==0 & aoi %in% c('TL', 'TR'))),	
		p_SS = n_SS / n,
		choseLL = mean(choseLL),
		.groups = 'keep') %>%
	dplyr::group_by(run_id) %>%
	dplyr::summarise(
		n_look_bottom = sum(n_bottom),
		p_look_bottom = mean(p_look_bottom),
		choseTop = mean(choseTop), 
		n_SS = mean(n_SS), 
		p_SS = mean(p_SS), 
		choseLL = mean(choseLL),
		.groups = 'keep')

# grouped = data_et %>% 
# 	merge_by_index(data_trial, 'choseTop') %>%
# 	merge_by_index(data_trial, 'choseLL') %>%
# 	merge_by_index(data_trial, 'LL_top') %>%
# 	filter(!is.na(aoi) & !aoi %in% c(0, '0')) %>%
# 	dplyr::group_by(run_id) %>%
# 	dplyr::summarise(
# 		n = n(),
# 		n_bottom = sum(aoi %in% c('BL', 'BR')), 
# 		p_look_bottom = n_bottom / n,
# 		choseTop = mean(choseTop), 
# 		n_SS = sum(
# 			(LL_top==1 & aoi %in% c('BL', 'BR')) |
# 			(LL_top==0 & aoi %in% c('TL', 'TR'))),	
# 		p_SS = n_SS / n, 
# 		choseLL = mean(choseLL),
# 		.groups = 'keep')

cor.test(grouped$p_look_bottom, grouped$choseTop) 
cor.test(grouped$p_SS, grouped$choseLL) 
```


# Last fixation
## Last fix top
```{r}
add_lastGazeTop = function(data_trial, data_et) {
    grouped_lastCoordinate = data_et %>%
    	filter(!aoi %in% c(0, '0') & !is.na(aoi)) %>%
        dplyr::group_by(run_id, trial_index) %>%
        slice(n()) %>%
    	mutate(
    		lastGazeTop = factor(as.numeric(aoi %in% c('TL', 'TR')),
    							 c('1', '0')),
        	lastGazeBottom = factor(as.numeric(aoi %in% c('BL', 'BR')),
        							c('1', '0')))
    
    data_trial = data_trial %>%
    	merge_by_index(grouped_lastCoordinate, 'lastGazeTop') %>%
    	merge_by_index(grouped_lastCoordinate, 'lastGazeBottom')
    
    return(data_trial)
}

data_trial = add_lastGazeTop(data_trial, data_et)

lastGaze_long <- data_trial %>%
    dplyr::group_by(run_id, lastGazeTop, withinTaskIndex) %>%
    dplyr::summarise(
    	choseTop=mean(choseTop),
    	.groups = 'keep') %>%
    dplyr::group_by(run_id, lastGazeTop) %>%
    dplyr::summarise(
        n_trials=n(),
    	choseTop=mean(choseTop),
        .groups = 'keep') 

lastGaze_long %>% filter(run_id %in% fix_best_runs)

# plot
ggplot(lastGaze_long %>% filter(run_id %in% c(choice_best_runs, fix_best_runs)), 
	   aes(x=lastGazeTop, y=choseTop)) +
    geom_violin(fill="gray", size=0) +
    stat_summary(fun=mean,geom="point",shape=45,size=10, color="white") +
    geom_text(x=1.5, y=1.02, label="***") + 
    annotate("segment",x=1, xend=2, y=1.01, yend=1.01) +
    theme_bw()+ylim(0,1.03)+xlab("") + 
    ylab("Proportion top choices") +
    xlab("last Fixation on Top AOIs") + 
    theme(text=element_text(size=20))
ggsave(file.path(path_results, 'et', 'time_bins', 'last_fix_top_vs_choice.png'),
			 width=5.5, height=5)
```

## Last fix Bottom
```{r}
lastGaze_long_bottom <- data_trial %>%
    dplyr::group_by(run_id, lastGazeBottom, withinTaskIndex) %>%
    dplyr::summarise(
    	choseTop=mean(choseTop),
    	.groups = 'keep') %>%
    dplyr::group_by(run_id, lastGazeBottom) %>%
    dplyr::summarise(
        n_trials=n(),
    	choseTop=mean(choseTop),
        .groups = 'keep') 

ggplot(lastGaze_long_bottom %>% filter(run_id %in% choice_best_runs), 
	   aes(x=lastGazeBottom, y=choseTop)) +
    geom_violin(fill="gray", size=0) +
    stat_summary(fun=mean,geom="point",shape=45,size=10, color="white") +
    geom_text(x=1.5, y=1.02, label="***") + 
    annotate("segment",x=1, xend=2, y=1.01, yend=1.01) +
    theme_bw()+ylim(0,1.03)+xlab("") + 
    ylab("Proportion top choices") +
    xlab("last Fixation on Bottom AOIs") + 
    theme(text=element_text(size=20))
```


## Last fix LL 
```{r}
add_lastGazeLL = function(data_trial, data_et) {
    grouped_lastCoordinate = data_et %>%
        dplyr::group_by(run_id, trial_index) %>%
        dplyr::summarise(
        	t_task = max(t_task), 
        	.groups = 'keep') %>%
        merge(data_et %>% 
                  dplyr::select(
                  	run_id, trial_index, t_task, 
      	   		    aoi, LL_top) %>%
                  filter(aoi!="0"), 
              by=c('run_id', 'trial_index', 't_task')) %>%
        mutate(lastGazeLL = factor(
        	as.numeric(
	            (aoi %in% c('TL', 'TR') & LL_top==1) |
	            (aoi %in% c('BL', 'BR') & LL_top==0)), 
        	c('1', '0')))
   
    if ('lastGazeLL' %in% names(data_trial)) {
        data_trial = data_trial %>% dplyr::select(!lastGazeLL)}
    data_trial = data_trial %>% 
        merge(
            grouped_lastCoordinate %>% 
                dplyr::select(run_id, trial_index, lastGazeLL), 
            by=c('run_id', 'trial_index'))
    
    return(data_trial)
}

data_trial = add_lastGazeLL(data_trial, data_et)


grouped_lastCoordinate = data_et %>%
    dplyr::group_by(run_id, trial_index) %>%
    dplyr::summarise(
    	t_task = max(t_task), 
    	.groups='keep') %>%
    merge(data_et %>% 
              dplyr::select(run_id, trial_index, t_task, aoi, LL_top) %>%
              filter(aoi!="0"), 
          by=c('run_id', 'trial_index', 't_task')) %>%
    mutate(lastGazeLL = as.numeric(
        (aoi %in% c('TL', 'TR') & LL_top==1) |
        (aoi %in% c('BL', 'BR') & LL_top==0)), 
    ) %>% 
    merge(data_trial %>%
              dplyr::select(run_id, trial_index, 
                            option_TL, option_TR, option_BR, option_BL,
                            choseLL),
          by=c('run_id', 'trial_index'))

grouped_lastCoordinate %>% head(25)

lastGaze_long <- data_trial %>% 
    dplyr::select(run_id, withinTaskIndex, lastGazeLL, choseLL) %>%
    dplyr::group_by(run_id, lastGazeLL, withinTaskIndex) %>%
    dplyr::summarise(
    	choseLL=mean(choseLL),
    	.groups = 'keep') %>%
    dplyr::group_by(run_id, lastGazeLL) %>%
    dplyr::summarise(
        n = n(),
        choseLL = mean(choseLL),
        .groups = 'keep') 

lastGaze_long %>% head(25)

subjects_noGaze = lastGaze_long %>% 
    group_by(run_id) %>%
    dplyr::summarise(
    	n_subj = n(), 
    	.groups = 'keep') %>%
    filter(n_subj<2) %>%
    arrange(run_id) %>%
    dplyr::pull(run_id)

t.test(
    choseLL ~ lastGazeLL,
    data=lastGaze_long %>% filter(!(run_id %in% subjects_noGaze)), 
    paired=TRUE)

ggplot(lastGaze_long, 
       aes(x=lastGazeLL, y=choseLL)) +
    geom_violin(fill="gray", size=0) +
    stat_summary(fun=mean,geom="point",shape=45,size=10, color="white") +
    geom_text(x=1.5, y=1.02, label="***") + 
    annotate("segment",x=1, xend=2, y=1.01, yend=1.01) +
    theme_bw()+ylim(0,1.03)+xlab("") + 
    ylab("Proportion LL choices") +
    xlab("last Fixation on LL AOIs") + 
    theme(text=element_text(size=20))
ggsave(file.path(path_results, 'et', 'time_bins', 'last_fix_ll_vs_choice.png'),
			 width=5.5, height=5)
```




## Last fix Amount
```{r}
add_lastGaze_amount = function(data_trial, data_et) {
    grouped_lastCoordinate = data_et %>%
        dplyr::group_by(run_id, trial_index) %>%
        dplyr::summarise(
        	t_task = max(t_task), 
        	.groups = 'keep') %>%
        merge(data_et %>% 
                  dplyr::select(run_id, trial_index, t_task, aoi, amountLeft) %>%
                  filter(aoi!="0"), 
              by=c('run_id', 'trial_index', 't_task')) %>%
        mutate(lastGaze_amount = as.numeric(
            (aoi %in% c('TL', 'BL') & amountLeft==1) |
            (aoi %in% c('TR', 'BR') & amountLeft==0)), 
        ) 
   
    data_trial = data_trial %>%
    	merge_by_index(grouped_lastCoordinate, 'lastGaze_amount')

    return(data_trial)
}

data_trial = add_lastGaze_amount(data_trial, data_et)

lastGaze_long <- data_trial %>% 
    dplyr::select(run_id, withinTaskIndex, lastGaze_amount, choseLL) %>%
    dplyr::group_by(run_id, lastGaze_amount, withinTaskIndex) %>%
    dplyr::summarise(
    	choseLL=mean(choseLL),
    	.groups = 'keep') %>%
    dplyr::group_by(run_id, lastGaze_amount) %>%
    dplyr::summarise(
        n = n(),
        choseLL = mean(choseLL),
        .groups = 'keep') 

lastGaze_long %>% head(5)

subjects_noGaze = lastGaze_long %>% 
    group_by(run_id) %>%
    dplyr::summarise(
    	n_subj = n(), 
    	.groups = 'keep') %>%
    filter(n_subj<2) %>%
    arrange(run_id) %>%
    dplyr::pull(run_id)

lastGaze_long$lastGaze_amount = factor(lastGaze_long$lastGaze_amount, c('1', '0'))
t.test(
    choseLL ~ lastGaze_amount,
    data=lastGaze_long %>% filter(!(run_id %in% subjects_noGaze)), 
    paired=TRUE)

ggplot(lastGaze_long, aes(x=lastGaze_amount, y=choseLL)) +
    geom_violin(fill="gray", size=0) +
    stat_summary(fun=mean,geom="point",shape=45,size=10, color="white") +
    geom_text(x=1.5, y=1.02, label="***") + 
    annotate("segment",x=1, xend=2, y=1.01, yend=1.01) +
    theme_bw()+ylim(0,1.03)+xlab("") + 
    ylab("Proportion LL choices") +
    xlab("last Fixation on amount AOIs") + 
    theme(text=element_text(size=20))
```


# Time bins
## Create bin dataset
```{r}
createTimeBins = function(data, nBins) {
    data$timeBin = 0
    progress_bar <- progress_estimated(length(unique(data$run_id)), 0)
    
    for (subject in unique(data$run_id)){
        df_subject = data %>% filter(run_id == subject)
        
        for (trial in unique(df_subject$withinTaskIndex)) {
            df_trial = df_subject %>% filter(withinTaskIndex == trial)
            
            this_timeBin = cut(
                df_trial$t_task, nBins,
                labels = c(1:nBins),
                include.lowest=TRUE)
            
            data = data %>%
                mutate(timeBin=replace(
                    timeBin, 
                    run_id==subject & withinTaskIndex==trial, 
                    this_timeBin))
        }
        progress_bar$pause(0.1)$tick()$print()
    }
    return(data)
}

data_et = createTimeBins(data_et, 5)

data_time_bins =  data_et %>%
	merge_by_index(data_trial, 'choseTop') %>%
    filter(!is.na(aoi) & !aoi %in% c(0, '0')) %>%
    mutate(
        lookTop = as.numeric(aoi %in% c('TL', 'TR')), 
        lookBottom = as.numeric(aoi %in% c('BL', 'BR'))) %>%
    dplyr::group_by(run_id, choseTop, timeBin) %>%
    dplyr::summarise(
        n_trials = n(),
        n_lookTop = sum(lookTop),
        n_lookBottom = sum(lookBottom),    
        p_lookTop = sum(lookTop)/n_trials,
        p_lookBottom = sum(lookBottom)/n_trials,
        .groups = 'keep') %>%
	mutate(
		choseTop = factor(choseTop, c('1', '0')), 
		timeBin = factor(timeBin)) %>%
	merge_by_subject(data_subject, 'window') %>%
	merge_by_subject(data_subject, 'fps') %>%
	dplyr::select(
		run_id, window, fps, choseTop, timeBin, n_trials, 
		n_lookTop, n_lookBottom, p_lookTop, p_lookBottom)

data_time_bins
```



## Plot function
```{r}
plot_et_time_bins = function(data_time_bins) {

	runs_not_enough_bins = data_time_bins %>%
	    group_by(run_id, choseTop) %>%
	    dplyr::summarise(
	    	n=length(unique(timeBin)),
	    	.groups = 'keep') %>%
	    filter(n<5) %>%
	    dplyr::pull(run_id)
	
	print('These runs have less than 5 time bins: ')
	print(runs_not_enough_bins)

	# t-test
	# for (bin in unique(data_time_bins$timeBin)) {
	#     print(t.test(p_lookTop ~ choseTop,
	#                  data=data_time_bins %>%
	#                      filter(timeBin==bin &
	#                             !(run_id %in% runs_not_enough_bins)),
	#                  paired=TRUE))
	# }
	
	
	bin_plot = ggplot(data_time_bins, 
		aes(x=factor(timeBin), y=p_lookTop, 
			fill=factor(choseTop, c('1', '0')))) + 
	geom_violin(alpha=.7, size=0, position="dodge") +
	stat_summary(
		fun=mean, geom="point", 
		shape=45, size=10, position=position_dodge(.9), 
		aes(color=factor(choseTop, c('1', '0')))) +
	scale_colour_manual( 
		values=c("1"="black", "0"="white"), name="", 
		labels=c("Chose top", "Chose bottom")) +
	scale_fill_grey(
		start=.3, end=.7, name="",
	  	labels=c("Chose top", "Chose bottom")) +
	xlab("Time bins") + ylab("Proportion looking top") +
	theme_bw() + 
	theme(text=element_text(size=20), legend.position="bottom")
	
	# Violin Plot
	# bin_plot = ggplot(data_time_bins, 
	#        aes(x=factor(timeBin), y=p_lookTop, fill=choseTop)) +
	#     geom_split_violin(alpha=0.7, size=1, position="dodge") +
	#     stat_summary(
	#         fun=mean, geom="point",
	#         shape=45,size=10,
	#         position=position_dodge(.9), 
	#         aes(color=factor(choseTop, c('1', '0')))) +
	#     theme_bw() + 
	#     theme(text=element_text(size=20), 
	#     legend.position="bottom") +
	#     ggtitle('Eye-tracking time bins') +
	#     scale_colour_manual(
	#         values=c("1"="black", "0"="white"), 
	#         name="", 
	#         labels=c("Chose Top", "Chose Bottom")) +
	#     scale_fill_grey(
	#         start=.3, end=.7, name="",
	#         labels=c("Chose Top", "Chose Bottom")) +
	#     ylab("Proportion looking top") +
	#     xlab("Time bins")
	
	print(bin_plot)
}
```

## All data
```{r}
plot_et_time_bins(data_time_bins)
ggsave(file.path(path_results, 'et', 'time_bins', 'bins_top_vs_bottom.png'), 
			 width=5.5, height=5)
```

## Only 'good participants'
```{r}
plot_et_time_bins(data_time_bins %>% filter(
	run_id %in% c(clustering_best_runs, choice_best_runs,fix_best_runs)))
ggsave(file.path(path_results, 'et', 'time_bins', 'bins_best_participants.png'), 
			 width=5.5, height=5)
```

## Reduce bins
```{r}
grouped_less_bins = data_et %>%
	createTimeBins(3) %>%
	merge_by_index(data_trial, 'choseTop') %>%
    filter(!is.na(aoi) & aoi!=0) %>%
    mutate(
        lookTop = as.numeric(aoi %in% c('TL', 'TR')), 
        lookBottom = as.numeric(aoi %in% c('BL', 'BR'))) %>%
    dplyr::group_by(run_id, choseTop, timeBin) %>%
    dplyr::summarise(
        n_trials = n(),
        n_lookTop = sum(lookTop),
        n_lookBottom = sum(lookBottom),    
        p_lookTop = sum(lookTop)/n_trials,
        p_lookBottom = sum(lookBottom)/n_trials,
        .groups = 'keep') %>%
	mutate(
		choseTop = factor(choseTop, c('1', '0')), 
		timeBin = factor(timeBin)) %>%
	merge_by_subject(data_subject, 'window') %>%
	merge_by_subject(data_subject, 'fps') %>%
	dplyr::select(
		run_id, window, fps, choseTop, timeBin, n_trials, 
		n_lookTop, n_lookBottom, p_lookTop, p_lookBottom)

plot_et_time_bins(grouped_less_bins)
ggsave(file.path(path_results, 'et', 'time_bins', 'bins_only_three.png'), 
			 width=5.5, height=5)

```

## Median
```{r}
ggplot(data_time_bins, 
		aes(x=factor(timeBin), y=p_lookTop, 
			fill=factor(choseTop, c('1', '0')))) + 
	geom_violin(alpha=.7, size=0, position="dodge") +
	stat_summary(
		fun=median, geom="point", 
		shape=45, size=10, position=position_dodge(.9), 
		aes(color=factor(choseTop, c('1', '0')))) +
	scale_colour_manual( 
		values=c("1"="black", "0"="white"), name="", 
		labels=c("Chose top", "Chose bottom")) +
	scale_fill_grey(
		start=.3, end=.7, name="",
	  	labels=c("Chose top", "Chose bottom")) +
	xlab("Time bins") + ylab("P looking top") +
	theme_bw() + 
	theme(text=element_text(size=20), legend.position="bottom")
ggsave(file.path(path_results, 'et', 'time_bins', 'bins_median.png'), 
			 width=5.5, height=5)

```

## Why are the tails so long? 
There are several participants 
```{r}
data_time_bins %>% 
	filter(
		choseTop==1 & 
	   	timeBin==5 &
		p_lookTop<0.2)

data_time_bins %>% 
	filter(
		choseTop==0 & 
	   	timeBin==5 &
		p_lookBottom<0.2)
```

## Participant Differences
Do specific participants distort the data? 
### Window
Some participants might have very small screens and look at the periphery
```{r}
ggplot(data_subject, aes(window))+
    geom_histogram(binwidth=100, alpha=.5, position="identity")+
    scale_fill_manual(values=c("palegreen","cornflowerblue"), name="") +
    theme_bw()+theme(text=element_text(size=40))

runs_large_windows = grouped_window %>%
	filter(window>2000) %>%
	dplyr::pull(run_id)

cat(paste('runs with large windows:', length(runs_large_windows), '\n'))

plot_et_time_bins(data_time_bins %>% 
				  	filter(run_id %in% runs_large_windows))
```


### FPS
When some participants do not look bottom. Is that because of fps? FPS does not seem to have an impact.
```{r}
# Trial level
grouped_bottom = data_et %>% 
	group_by(run_id, trial_index) %>%
	dplyr::summarise(
		n_bottom = sum(y < 0.5),
		.groups = 'keep') %>%
	merge(
		data_trial %>% dplyr::select(run_id, trial_index, fps),
		by=c('run_id', 'trial_index')) %>% 
	filter(!is.na(fps) & !is.na(n_bottom))

cor.test(grouped_bottom$n_bottom, grouped_bottom$fps) 

ggplot(grouped_bottom, 
       aes(x=fps, y=n_bottom)) +
		geom_point(size=2.5, aes(alpha=.5)) +
		guides(alpha=FALSE,color=FALSE, shape=FALSE) +
		theme(text=element_text(size=20)) + 
	    ggtitle('N bottom gaze points vs. fps (trial level)') + 
		theme(plot.title = element_text(size = 15, face = "bold"))

# Subject level
grouped = data_et %>%
	mutate(look_top = factor(
		as.numeric(y > 0.5))) %>%
	group_by(run_id, look_top) %>%
	dplyr::summarise(
		n = n(),
		.groups = 'keep') %>%
	merge(
		data_subject %>% dplyr::select(run_id, fps),
		by=c('run_id')) %>% 
	filter(!is.na(fps) & !is.na(n))

cor.test(grouped_bottom$n_bottom, grouped_bottom$fps) 

ggplot(grouped, 
       aes(x=fps, y=n, color=look_top)) +
	geom_point(size=2.5) +
	theme(text=element_text(size=20)) + 
    ggtitle('N gaze points vs. fps (subject level)') + 
		theme(plot.title = element_text(size = 15, face = "bold"))

## Filter high fps
fps_threshold = 15

runs_high_fps = data_subject %>%
	filter(fps >= fps_threshold) %>%
	dplyr::pull(run_id)
cat(paste('runs with fps >=', fps_threshold, ':', length(runs_high_fps)))

plot_et_time_bins(data_time_bins %>% filter(run_id %in% runs_high_fps))
ggsave(file.path(path_results, 'et', 'time_bins', 'bins_fps_high.png'), 
			 width=5.5, height=5)

runs_low_fps = data_subject %>%
	filter(fps < fps_threshold) %>%
	dplyr::pull(run_id)
cat(paste('runs with fps <', fps_threshold, ':', length(runs_low_fps)))

plot_et_time_bins(data_time_bins %>% filter(run_id %in% runs_low_fps))
ggsave(file.path(path_results, 'et', 'time_bins', 'bins_fps_low.png'), 
			 width=5.5, height=5)
```

```{r}
fps_threshold = 20

runs_high_fps = data_subject %>%
	filter(fps>fps_threshold) %>%
	dplyr::pull(run_id)

print(paste('Runs: fps >', fps_threshold, ': ', length(runs_high_fps)))

ggplot(data_time_bins %>% filter(run_id %in% runs_high_fps), 
	aes(x=factor(timeBin), y=p_lookTop, 
		fill=factor(choseTop, c('1', '0')))) + 
	geom_violin(alpha=.7, size=0, position="dodge") +
	stat_summary(
		fun=mean, geom="point", 
		shape=45, size=10, position=position_dodge(.9), 
		aes(color=factor(choseTop, c('1', '0')))) +
	scale_colour_manual(
		values=c("1"="black", "0"="white"), name="", 
		labels=c("Chose top", "Chose bottom")) +
	scale_fill_grey(
		start=.3, end=.7, name="",
	  	labels=c("Chose top", "Chose bottom")) +
	xlab("Time bins") + ylab("Proportion looking top") +
	theme_bw() + theme(text=element_text(size=20), legend.position="bottom")
ggsave(file.path(path_results, 'et', 'time_bins', 'bins_top_vs_bottom_fps.png'),
			 width=5.5, height=5)
```



### Data quality
```{r}
ggplot(data_subject, aes(offset))+
    geom_histogram(binwidth=0.025, alpha=.5, position="identity")+
    scale_fill_manual(values=c("palegreen","cornflowerblue"), name="") +
    theme_bw()+theme(text=element_text(size=40))

ggplot(data_subject, aes(precision))+
    geom_histogram(binwidth=0.01, alpha=.5, position="identity")+
    scale_fill_manual(values=c("palegreen","cornflowerblue"), name="") +
    theme_bw()+theme(text=element_text(size=40))

ggplot(data_subject, aes(fps))+
    geom_histogram(binwidth=1, alpha=.5, position="identity")+
    scale_fill_manual(values=c("palegreen","cornflowerblue"), name="") +
    theme_bw()+theme(text=element_text(size=40))


runs_plot = data_subject %>% 
	filter(
		offset <= 0.15 & 
		precision <= 0.06) %>%
	dplyr::pull(run_id)

print(paste('N runs:', length(runs_plot)))

plot_et_time_bins(data_time_bins %>% filter(run_id %in% runs_plot))
ggsave(file.path(path_results, 'et', 'time_bins', 'bins_quality_high.png'), 
			 width=5.5, height=5)

runs_plot = data_subject %>% 
	filter(
		offset > 0.15 & 
		precision > 0.06) %>%
	dplyr::pull(run_id)

print(paste('N runs:', length(runs_plot)))

plot_et_time_bins(data_time_bins %>% filter(run_id %in% runs_plot))
ggsave(file.path(path_results, 'et', 'time_bins', 'bins_quality_low.png'), 
			 width=5.5, height=5)
```

### What if participants do not look at the top option
```{r}
# Pos. ~ looking top --> top - bottom
grouped_tb_index = data_et %>% group_by(run_id, trial_index) %>%
	dplyr::summarise(
		look_top = sum(aoi %in% c('TL', 'TR')),
		look_bottom = sum(aoi %in% c('BL', 'BR')),
		tb_index = (look_top-look_bottom) / (look_top+look_bottom),
		.groups='keep')

grouped_tb_index

data_trial = merge_by_index(data_trial, grouped_tb_index, 'tb_index')

ggplot(data_trial, aes(tb_index)) +
    geom_histogram(binwidth=.1, alpha=.5, position="identity") +
    scale_fill_manual(values=c("palegreen","cornflowerblue"), name="") +
    theme_bw() + 
    ggtitle('Histogram of top_bottom relation (trial level)') + 
	theme(plot.title = element_text(size = 15, face = "bold"))
ggsave(file.path(path_results, 'et', 'time_bins', 'tb_index_hist.png'), 
			 width=5.5, height=5)

# Subject level
grouped_tb_index = data_trial %>%
	group_by(run_id) %>%
	dplyr::summarise(
		tb_index = mean(tb_index),
		.groups = 'keep')

data_subject = merge_mean_by_subject(data_subject, grouped_tb_index, 'tb_index')

ggplot(data_subject, aes(tb_index))+
    geom_histogram(binwidth=.1, alpha=.5, position="identity")+
    scale_fill_manual(values=c("palegreen","cornflowerblue"), name="") +
    theme_bw() + 
    ggtitle('Histogram of top_bottom relation (subject level)') + 
	theme(plot.title = element_text(size = 15, face = "bold"))
ggsave(file.path(path_results, 'et', 'time_bins', 'tb_index_participants_hist.png'), 
			 width=5.5, height=5)
```

### Only those trials who look at both options
When filtering for top_bottom_index, I get a tendency towards the middle
```{r}
bins_cleaned_tb_index =  data_et %>%
	merge_by_index(data_trial, 'choseTop') %>%
	merge_by_index(data_trial, 'tb_index') %>%
    filter(
    	!is.na(aoi) & aoi!=0 &
	   	tb_index > -0.99 & tb_index < 0.99) %>%
    mutate(
        lookTop = as.numeric(aoi %in% c('TL', 'TR')), 
        lookBottom = as.numeric(aoi %in% c('BL', 'BR'))) %>%
    dplyr::group_by(run_id, choseTop, timeBin) %>%
    dplyr::summarise(
        n = n(),
        n_lookTop = sum(lookTop),
        n_lookBottom = sum(lookBottom),    
        p_lookTop = sum(lookTop)/n,
        p_lookBottom = sum(lookBottom)/n,
        .groups = 'keep') %>%
	mutate(
		choseTop = factor(choseTop, c('1', '0')), 
		timeBin = factor(timeBin))

# Clean trials




print(paste(
	'excluded', 
	data_trial %>% 
		filter(tb_index %in% c(-1, 1)) %>% 
		nrow(),
	'trials with tb_index in c(-1, 1). ',
	data_trial %>% 
		filter(!tb_index %in% c(-1, 1)) %>% 
		nrow(),
	'remain. '))


plot_et_time_bins(bins_cleaned_tb_index)
ggsave(file.path(path_results, 'et', 'time_bins', 'bins_cleaned_tb_index_trials.png'), 
			 width=5.5, height=5)

# Clean runs
runs_balanced_tb = data_subject %>%
	filter(tb_index > -0.8 & tb_index < 0.8) %>%
	dplyr::pull(run_id)
print(paste('N runs: ', length(runs_balanced_tb)))

plot_et_time_bins(data_time_bins %>% filter(run_id %in% runs_balanced_tb))
ggsave(file.path(path_results, 'et', 'time_bins', 'bins_cleaned_tb_index_participants.png'), 
			 width=5.5, height=5)
```




### What about those participants who never look down?
Are they less likely to choose the bottom option? Those trials, who have almost all gaze points in the upper half of the screen, are like 50% for choosing the top option. Same way vice versa, those trials who have almost all gaze points in the lower half, only had a chance of 60% for choosing the bottom areas
```{r}
grouped_top_bottom = data_et %>% 
	merge_by_index(data_trial, 'choseTop') %>%
	group_by(run_id, trial_index) %>%
	dplyr::summarise(
		n_top = sum(y > 0.5),
		n_bottom = sum(y < 0.5),
		choseTop = choseTop, 
		.groups = 'keep') %>%
	distinct()

only_top_n = grouped_top_bottom %>%
	filter(n_top > 25 & n_bottom < 1) %>% 
	nrow()

only_top_mean_choseTop = grouped_top_bottom %>%
	filter(n_top > 25 & n_bottom < 1) %>%
	dplyr::pull(choseTop) %>%
	mean()

cat(paste(
		'Those trials, where participants had more than 25 gaze points',
		'on the top option and zero gaze points on the bottom, had a ',
		'probability of',
		round(only_top_mean_choseTop, 2),
		'(', only_top_n, ' trials)',
		'for choosing the top option.'))

only_bottom_n = grouped_top_bottom %>%
	filter(n_top < 1 & n_bottom > 25) %>% 
	nrow()

only_bottom_mean_choseTop = grouped_top_bottom %>%
	filter(n_top < 1 & n_bottom > 25) %>%
	dplyr::pull(choseTop) %>%
	mean()

cat(paste(
		'Those trials, where participants had more than 25 gaze points',
		'on the bottom option and zero gaze points on the top, had a ',
		'probability of',
		round(only_bottom_mean_choseTop, 2),
		'(', only_bottom_n, ' trials)',
		'for choosing the top option.'))

grouped = data_trial %>%
	filter(tb_index %in% c(-1, 1)) %>%
	group_by(tb_index, run_id) %>%
	dplyr::summarise(
		n_trials = n(), 
		choseTop = mean(key_press==38),
		choseLL = mean(choseLL),
		.groups = 'keep') %>% 
	group_by(tb_index) %>%
	dplyr::summarise(
		n_participants = n(),
		n_trials = sum(n_trials),
		top = mean(choseTop), 
		top_std = sd(choseTop),
		LL = mean(choseLL), 
		LL_std = sd(choseLL),
		.groups='keep')

grouped

write.csv(grouped, file.path('results', 'tables', 'choice_task', 'biased_gaze.csv'))
```





### Reaction time
What if participants do not take the time to look at options and consider alternatives. Let's only look at those with 
```{r}
bins_longer_rts =  data_et %>%
	merge_by_index(data_trial, 'choseTop') %>%
	merge_by_index(data_trial, 'trial_duration_exact') %>%
    filter(
    	!is.na(aoi) & aoi!=0 &
    	trial_duration_exact > 1000) %>%
    mutate(
        lookTop = as.numeric(aoi %in% c('TL', 'TR')), 
        lookBottom = as.numeric(aoi %in% c('BL', 'BR'))) %>%
    dplyr::group_by(run_id, choseTop, timeBin) %>%
    dplyr::summarise(
        n = n(),
        n_lookTop = sum(lookTop),
        n_lookBottom = sum(lookBottom),    
        p_lookTop = sum(lookTop)/n,
        p_lookBottom = sum(lookBottom)/n,
        .groups = 'keep') %>%
	mutate(
		choseTop = factor(choseTop, c('1', '0')), 
		timeBin = factor(timeBin))

print(paste('How much data?', 
			length(unique(bins_longer_rts$run_id)),
			'runs ,',
			nrow(bins_longer_rts),
			'trials'))

plot_et_time_bins(bins_longer_rts)
```

### Left vs. right time bins
```{r}
bins_left_vs_right = data_et %>%
	merge_by_index(data_trial, 'choseLL') %>%
	merge_by_index(data_trial, 'amountLeft') %>%
    filter(!is.na(aoi) & aoi!=0) %>%
    mutate(
        look_amount = as.numeric(
        	(amountLeft==1 & aoi %in% c('TL', 'BL')) |
        	(amountLeft==0 & aoi %in% c('TR', 'BR')))) %>%
    dplyr::group_by(run_id, choseLL, timeBin) %>%
    dplyr::summarise(
        n = n(),
        n_look_amount = sum(look_amount),  
        p_look_amount = sum(look_amount)/n,
        .groups = 'keep') %>%
	mutate(
		choseLL = factor(choseLL, c('1', '0')), 
		timeBin = factor(timeBin))

bins_left_vs_right

ggplot(bins_left_vs_right, 
		aes(x=factor(timeBin), y=p_look_amount, 
			fill=choseLL)) + 
	geom_violin(alpha=.7, size=0, position="dodge") +
	stat_summary(
		fun=mean, geom="point", 
		shape=45, size=10, position=position_dodge(.9), 
		aes(color=choseLL)) +
	scale_colour_manual( 
		values=c("1"="black", "0"="white"), name="", 
		labels=c("Chose LL", "Chose SS")) +
	scale_fill_grey(
		start=.3, end=.7, name="",
	  	labels=c("Chose LL", "Chose SS")) +
	xlab("Time bins") + ylab("Proportion looking Amount") +
	theme_bw() + 
	theme(text=element_text(size=20), legend.position="bottom")

```


## Eyetracking data bins
```{r}
create_eyeTracking_Bins = function(data, nBins) {
    data$et_bin = 0
    
    progress_bar <- progress_estimated(length(unique(data$run_id)), 0)
    
    for (subject in unique(data$run_id)){
    
        df_subject = data %>% filter(run_id == subject)
        
        for (trial in unique(df_subject$withinTaskIndex)) {
            df_trial = df_subject %>% filter(withinTaskIndex == trial)
            
            this_et_bin = cut(
                c(1:nrow(df_trial)), 
                nBins,
                labels = c(1:nBins),
                include.lowest=TRUE)
            
            data = data %>%
                mutate(et_bin=replace(
                    et_bin, 
                    run_id==subject & withinTaskIndex==trial, 
                    this_et_bin))
        }
        
        progress_bar$pause(0.1)$tick()$print()
        
    }
    return(data)
}


data_et = create_eyeTracking_Bins(data_et, 5)
data_et %>%
    group_by(run_id, withinTaskIndex, et_bin) %>%
    dplyr::summarise(
    	n=n(), 
    	.groups = 'keep') %>% 
	head(5)

data_et %>%
    dplyr::select(run_id, withinTaskIndex, et_bin, t_task) %>%
    arrange(run_id, withinTaskIndex, et_bin, t_task) %>% 
	head(5)

data_et_bins_new = data_et %>%
	merge(
		data_trial %>% dplyr::select(run_id, trial_index, choseTop),
		by=c('run_id', 'trial_index')) %>%
    mutate(
        lookTop = as.numeric(aoi %in% c('TL', 'TR')), 
        lookBottom = as.numeric(aoi %in% c('BL', 'BR')),
        null_aoi = as.numeric(aoi=='0')) %>%
    dplyr::group_by(run_id, choseTop, et_bin) %>%
    dplyr::summarise(
        n = n(),
        n_lookTop = sum(lookTop),
        n_lookBottom = sum(lookBottom), 
        n_null_aoi = sum(null_aoi),
        p_lookTop = sum(lookTop)/n,
        p_lookBottom = sum(lookBottom)/n,
        p_null_aoi = sum(null_aoi)/n,
        .groups = 'keep') %>%
	mutate(
		choseTop = factor(choseTop, c('1', '0')),
		et_bin = factor(et_bin))

ggplot(data_et_bins_new %>% filter(run_id %in% clustering_best_runs), 
		aes(x=factor(et_bin), y=p_lookTop, 
			fill=factor(choseTop, c('1', '0')))) + 
	geom_violin(alpha=.7, size=0, position="dodge") +
	stat_summary(
		fun=mean, geom="point", 
		shape=45, size=10, position=position_dodge(.9), 
		aes(color=factor(choseTop, c('1', '0')))) +
	scale_colour_manual( 
		values=c("1"="black", "0"="white"), name="", 
		labels=c("Chose top", "Chose bottom")) +
	scale_fill_grey(
		start=.3, end=.7, name="",
	  	labels=c("Chose top", "Chose bottom")) +
	xlab("Time bins") + ylab("Proportion looking top") +
	theme_bw() + 
	theme(text=element_text(size=20), legend.position="bottom")
```



