---
title: 'Analyzing eye-tracking behavior vs. choices'
output:
  html_document:
    df_print: paged
---

# Setup
```{r, setup, message=FALSE, warning=FALSE}
root = "C:/Users/User/GitHub/WebET_Analysis"

path_results = file.path(root, 'results', 'plots', 'choice_task')
# Create directory for plots
dir.create(file.path(path_results, 'et', 'time_bins'),
		   showWarnings = FALSE)

dir.create(file.path(path_results, 'et', 'last_fix'),
		   showWarnings = FALSE)

knitr::opts_knit$set(root.dir = normalizePath(file.path('..', '..')))

knitr::opts_knit$get("root.dir")


source(file.path(root, 'utils', 'r', 'geom_split_violin.R'))
source(file.path(root, 'utils', 'r', 'merge_by_subject.R'))
source(file.path(root, 'utils', 'r', 'merge_mean_by_subject.R'))
source(file.path(root, 'utils', 'r', 'merge_by_index.R'))
source(file.path(root, 'utils', 'r', 'summarize_datasets.R'))
source(file.path(root, 'utils', 'r', 'get_packages.R'))
source(file.path(root, 'utils', 'r', 'remove_runs.R'))
source(file.path(root, 'utils', 'r', 'add_x_count.R'))
source(file.path(root, 'utils', 'r', 'add_new_aoi.R'))
source(file.path(root, 'utils', 'r', 'create_time_bins.R'))
source(file.path(root, 'utils', 'r', 'plot_et_time_bins.R'))
source(file.path(root, 'utils', 'r', 'add_last_fix_top_bottom.R'))
source(file.path(root, 'utils', 'r', 'add_last_fix_ll_amount.R'))

get_packages(c(
	'plyr',
	'dplyr', 
	"effsize",
	'e1071',
	"ggplot2",
	"ggsignif",
	'knitrProgressBar',
	'lme4',
	'progress',
	'QuantPsyc',
	"RColorBrewer",
	'reshape2',
	'tidyr'))

print(getwd())
```

# Specific participants
```{r}
choice_best_runs = c(7,96,126,130,162,177,212,238,288,427)

fix_best_runs = c(16,41,126,162,199,205,253,299,318,347,378,414,418,420,427,
				  437,491)

clustering_best_runs = c(7,32,45,48,63,96,126,128,130,197,205,212,238,275,
						 280,288,344,420)
```


# Prep data 
## Load data
```{r, load_datasets}
path=file.path(root, 'data', 'choice_task', 'cleaned')
data_subject = read.csv(file.path(path, 'data_subject.csv'))
data_trial = read.csv(file.path(path, 'data_trial.csv'))
data_et = read.csv(file.path(path, 'data_et.csv'))

summarize_datasets(data_et, data_trial, data_subject)
```

## Check AOI (optionally new AOIs)
```{r}
data_et = add_new_aoi(data_et, 0.4, 0.4)

ggplot(data_et %>% filter(aoi %in% c('TL', 'TR', 'BL', 'BR')) %>% head(10000), 
	   aes(x=x, y=y)) +
    geom_point(size=2.5, aes(alpha=.5))+
    guides(alpha=FALSE,color=FALSE, shape=FALSE)+
    theme_bw() + 
	xlim(0, 1) + ylim(1, 0) +
    scale_colour_grey() + 
    theme(text=element_text(size=20)) +
    xlab("x") + ylab("y") +
    ggtitle('AOIs') 
```

## Window
```{r}
add_window = function(data_subject, data_trial) {

	grouped_window = data_trial %>%
		mutate(window_diagonal = sqrt(
			window_width * window_width + 
			window_height * window_height)) %>%
		group_by(run_id) %>%
		dplyr::summarise(
			window = max(window_diagonal),
			.groups = 'keep')
	
	data_subject = merge_by_subject(data_subject, grouped_window, 'window')

	return(data_subject)
}

data_subject = add_window(data_subject, data_trial)
```



# Gaze points ~ choice
```{r}
grouped_trial = data_et %>% 
	merge_by_index(data_trial, 'choseTop') %>%
	merge_by_index(data_trial, 'choseLL') %>%
	merge_by_index(data_trial, 'LL_top') %>%
	merge_by_index(data_trial, 'amountLeft') %>%
	filter(aoi %in% c('TL', 'TR', 'BL', 'BR')) %>% 
	dplyr::group_by(run_id, trial_index) %>%
	dplyr::summarise(
		n = n(),
		n_look_top = sum(aoi %in% c('TL', 'TR')), 
		p_look_top = n_look_top / n,
		n_look_ll = sum(
			(aoi %in% c('TL', 'TR') & LL_top==1) |
			(aoi %in% c('BL', 'BR') & LL_top==0)),	
		p_look_ll = n_look_ll / n,
		n_look_amount = sum(
			(aoi %in% c('TL', 'BL') & amountLeft == 1)  |
			(aoi %in% c('TR', 'BR') & amountLeft == 0)),
		p_look_amount = n_look_amount / n,
		choseTop = mean(choseTop), 
		choseLL = mean(choseLL),
		.groups = 'keep')

grouped_run = grouped_trial %>%
	dplyr::group_by(run_id) %>%
	dplyr::summarise(
		n_look_top = mean(n_look_top),
		p_look_top = mean(p_look_top),
		n_look_ll = mean(n_look_ll), 
		p_look_ll = mean(p_look_ll), 
		n_look_amount = mean(n_look_amount),
		p_look_amount = mean(p_look_amount),
		choseTop = mean(choseTop), 
		choseLL = mean(choseLL),
		.groups = 'keep')

grouped_run

cor.test(grouped_run$p_look_top, grouped_run$choseTop) 
cor.test(grouped_run$p_look_ll, grouped_run$choseLL) 
cor.test(grouped_run$p_look_amount, grouped_run$choseLL) 

data_subject %>%
	dplyr::select(run_id, optionIndex, attributeIndex, payneIndex, 
				  choseLL) %>%
	arrange(choseLL)

ggplot(grouped_trial, aes(x=factor(choseLL), y=p_look_amount)) + 
    geom_boxplot() +
	ggtitle(('Looking at amount vs. time information and choosing LL vs. SS'))
```


# Last fixation
## Last fix top
```{r}
data_trial = add_last_fix_top_bottom(data_trial, data_et)

lastGaze_long <- data_trial %>%
    dplyr::group_by(run_id, last_fix_top, withinTaskIndex) %>%
    dplyr::summarise(
    	choseTop=mean(choseTop),
    	.groups = 'keep') %>%
    dplyr::group_by(run_id, last_fix_top) %>%
    dplyr::summarise(
        n_trials=n(),
    	choseTop=mean(choseTop),
        .groups = 'keep') 

sel_runs = lastGaze_long %>% 
	filter(last_fix_top == 1) %>%
	filter(choseTop < 0.6) %>%
	dplyr::pull(run_id)

data_subject %>% 
	filter(run_id %in% sel_runs)


t.test(choseTop ~ last_fix_top,
	   data=lastGaze_long,
	   paired=TRUE)
	
cohen.d(choseTop ~ last_fix_top, pooled=TRUE, paired=TRUE, 
	data=lastGaze_long)

# plot
ggplot(lastGaze_long, 
	   aes(x=last_fix_top, y=choseTop)) +
    geom_violin(fill="gray", size=0) +
    stat_summary(fun=mean,geom="point",shape=45,size=10, color="white") +
    geom_text(x=1.5, y=1.02, label="***") + 
    annotate("segment",x=1, xend=2, y=1.01, yend=1.01) +
    theme_bw()+ylim(0,1.03)+xlab("") + 
    ylab("Proportion top choices") +
    xlab("last Fixation on Top AOIs") + 
    theme(text=element_text(size=20))
ggsave(file.path(path_results, 'et', 'last_fix', 'top_vs_choice.png'),
			 width=5.5, height=5)
```

## Last fix Bottom
```{r}
last_fix_long_bottom = data_trial %>%
    dplyr::group_by(run_id, last_fix_bottom, withinTaskIndex) %>%
    dplyr::summarise(
    	choseTop=mean(choseTop),
    	.groups = 'keep') %>%
    dplyr::group_by(run_id, last_fix_bottom) %>%
    dplyr::summarise(
        n_trials=n(),
    	choseTop=mean(choseTop),
        .groups = 'keep') 

ggplot(last_fix_long_bottom, 
	   aes(x=last_fix_bottom, y=choseTop)) +
    geom_violin(fill="gray", size=0) +
    stat_summary(fun=mean,geom="point",shape=45,size=10, color="white") +
    geom_text(x=1.5, y=1.02, label="***") + 
    annotate("segment",x=1, xend=2, y=1.01, yend=1.01) +
    theme_bw()+ylim(0,1.03)+xlab("") + 
    ylab("Proportion top choices") +
    xlab("last Fixation on Bottom AOIs") + 
    theme(text=element_text(size=20))
ggsave(file.path(path_results, 'et', 'last_fix', 'bottom_vs_choice.png'),
			 width=5.5, height=5)
```


## Last fix LL 
```{r}
data_trial = add_last_fix_ll_amount(data_trial, data_et)

lastGaze_long <- data_trial %>% 
    dplyr::select(run_id, withinTaskIndex, last_fix_ll, choseLL) %>%
    dplyr::group_by(run_id, last_fix_ll, withinTaskIndex) %>%
    dplyr::summarise(
    	choseLL=mean(choseLL),
    	.groups = 'keep') %>%
    dplyr::group_by(run_id, last_fix_ll) %>%
    dplyr::summarise(
        n = n(),
        choseLL = mean(choseLL),
        .groups = 'keep') 

subjects_noGaze = lastGaze_long %>% 
    group_by(run_id) %>%
    dplyr::summarise(
    	n_subj = n(), 
    	.groups = 'keep') %>%
    filter(n_subj<2) %>%
    arrange(run_id) %>%
    dplyr::pull(run_id)

t.test(
    choseLL ~ last_fix_ll,
    data=lastGaze_long %>% filter(!(run_id %in% subjects_noGaze)), 
    paired=TRUE)

ggplot(lastGaze_long, 
       aes(x=last_fix_ll, y=choseLL)) +
    geom_violin(fill="gray", size=0) +
    stat_summary(fun=mean,geom="point",shape=45,size=10, color="white") +
    geom_text(x=1.5, y=1.02, label="***") + 
    annotate("segment",x=1, xend=2, y=1.01, yend=1.01) +
    theme_bw()+ylim(0,1.03)+xlab("") + 
    ylab("Proportion LL choices") +
    xlab("last Fixation on LL AOIs") + 
    theme(text=element_text(size=20))
ggsave(file.path(path_results, 'et', 'last_fix', 'll_vs_choice.png'),
			 width=5.5, height=5)
```


## Last fix Amount
```{r}
lastGaze_long <- data_trial %>% 
    dplyr::select(run_id, withinTaskIndex, last_fix_amount, choseLL) %>%
    dplyr::group_by(run_id, last_fix_amount, withinTaskIndex) %>%
    dplyr::summarise(
    	choseLL=mean(choseLL),
    	.groups = 'keep') %>%
    dplyr::group_by(run_id, last_fix_amount) %>%
    dplyr::summarise(
        n = n(),
        choseLL = mean(choseLL),
        .groups = 'keep') 

subjects_noGaze = lastGaze_long %>% 
    group_by(run_id) %>%
    dplyr::summarise(
    	n_subj = n(), 
    	.groups = 'keep') %>%
    filter(n_subj<2) %>%
    arrange(run_id) %>%
    dplyr::pull(run_id)

t.test(
    choseLL ~ last_fix_amount,
    data=lastGaze_long %>% filter(!(run_id %in% subjects_noGaze)), 
    paired=TRUE)

ggplot(lastGaze_long, aes(x=last_fix_amount, y=choseLL)) +
    geom_violin(fill="gray", size=0) +
    stat_summary(fun=mean,geom="point",shape=45,size=10, color="white") +
    geom_text(x=1.5, y=1.02, label="***") + 
    annotate("segment",x=1, xend=2, y=1.01, yend=1.01) +
    theme_bw()+ylim(0,1.03)+xlab("") + 
    ylab("Proportion LL choices") +
    xlab("last Fixation on amount AOIs") + 
    theme(text=element_text(size=20))
ggsave(file.path(path_results, 'et', 'last_fix', 'ss_vs_choice.png'),
			 width=5.5, height=5)
```


# Time bins
## Create bin dataset
```{r}
data_et = create_time_bins(data_et, 5)

data_time_bins =  data_et %>%
	merge_by_index(data_trial, 'choseTop') %>%
    filter(!is.na(aoi) & !aoi %in% c(0, '0')) %>%
    mutate(
        lookTop = as.numeric(aoi %in% c('TL', 'TR')), 
        lookBottom = as.numeric(aoi %in% c('BL', 'BR'))) %>%
    dplyr::group_by(run_id, choseTop, time_bin) %>%
    dplyr::summarise(
        n_trials = n(),
        n_lookTop = sum(lookTop),
        n_lookBottom = sum(lookBottom),    
        p_lookTop = sum(lookTop)/n_trials,
        p_lookBottom = sum(lookBottom)/n_trials,
        .groups = 'keep') %>%
	mutate(
		choseTop = factor(choseTop, c('1', '0')), 
		time_bin = factor(time_bin)) %>%
	merge_by_subject(data_subject, 'window') %>%
	merge_by_subject(data_subject, 'fps') %>%
	dplyr::select(
		run_id, window, fps, choseTop, time_bin, n_trials, 
		n_lookTop, n_lookBottom, p_lookTop, p_lookBottom)

data_time_bins
```



## All data
```{r}
plot_et_time_bins(data_time_bins)

ggplot(data_time_bins, 
		aes(x=factor(time_bin), y=p_lookTop, 
			fill=factor(choseTop, c('1', '0')))) + 
	geom_violin(alpha=.7, size=0, position="dodge") +
	stat_summary(
		fun=mean, geom="point", 
		shape=45, size=10, position=position_dodge(.9), 
		aes(color=factor(choseTop, c('1', '0')))) +
	scale_colour_manual( 
		values=c("1"="black", "0"="white"), name="", 
		labels=c("Chose top", "Chose bottom")) +
	scale_fill_grey(
		start=.3, end=.7, name="",
	  	labels=c("Chose top", "Chose bottom")) +
	xlab("Time bins") + ylab("Proportion looking top") +
	ylim(0, 1) + 
	geom_text(x=5, y=1.01, label="***") + 
	annotate("segment",x=4.7, xend=5.3, y=1, yend=1) +
	theme_bw() + 
	theme(text=element_text(size=20), legend.position="bottom")
ggsave(file.path(path_results, 'et', 'time_bins', 'top_vs_bottom.png'), 
			 width=5.5, height=5)
```


## Reduce bins
```{r}
grouped_less_bins = data_et %>%
	create_time_bins(3) %>%
	merge_by_index(data_trial, 'choseTop') %>%
    filter(!is.na(aoi) & aoi!=0) %>%
    mutate(
        lookTop = as.numeric(aoi %in% c('TL', 'TR')), 
        lookBottom = as.numeric(aoi %in% c('BL', 'BR'))) %>%
    dplyr::group_by(run_id, choseTop, time_bin) %>%
    dplyr::summarise(
        n_trials = n(),
        n_lookTop = sum(lookTop),
        n_lookBottom = sum(lookBottom),    
        p_lookTop = sum(lookTop)/n_trials,
        p_lookBottom = sum(lookBottom)/n_trials,
        .groups = 'keep') %>%
	mutate(
		choseTop = factor(choseTop, c('1', '0')), 
		time_bin = factor(time_bin)) %>%
	merge_by_subject(data_subject, 'window') %>%
	merge_by_subject(data_subject, 'fps') %>%
	dplyr::select(
		run_id, window, fps, choseTop, time_bin, n_trials, 
		n_lookTop, n_lookBottom, p_lookTop, p_lookBottom)

plot_et_time_bins(grouped_less_bins)
ggsave(file.path(path_results, 'et', 'time_bins', 'only_three_bins.png'), 
			 width=5.5, height=5)

```


## Why are the tails so long? 
There are several participants 
```{r}
data_time_bins %>% 
	filter(
		choseTop==1 & 
	   	time_bin==5 &
		p_lookTop<0.2)

data_time_bins %>% 
	filter(
		choseTop==0 & 
	   	time_bin==5 &
		p_lookBottom<0.2)
```

## Participant Differences
Do specific participants distort the data? 
### Window
Some participants might have very small screens and look at the periphery
```{r}
ggplot(data_subject, aes(window))+
    geom_histogram(binwidth=100, alpha=.5, position="identity")+
    scale_fill_manual(values=c("palegreen","cornflowerblue"), name="") +
    theme_bw()+theme(text=element_text(size=40))

runs_large_windows = grouped_window %>%
	filter(window>2000) %>%
	dplyr::pull(run_id)

cat(paste('runs with large windows:', length(runs_large_windows), '\n'))

plot_et_time_bins(data_time_bins %>% 
				  	filter(run_id %in% runs_large_windows))
```


### FPS
When some participants do not look bottom. Is that because of fps? FPS does not seem to have an impact.
```{r}
# Trial level
grouped_bottom = data_et %>% 
	group_by(run_id, trial_index) %>%
	dplyr::summarise(
		n_bottom = sum(y < 0.5),
		.groups = 'keep') %>%
	merge(
		data_trial %>% dplyr::select(run_id, trial_index, fps),
		by=c('run_id', 'trial_index')) %>% 
	filter(!is.na(fps) & !is.na(n_bottom))

cor.test(grouped_bottom$n_bottom, grouped_bottom$fps) 

ggplot(grouped_bottom, 
       aes(x=fps, y=n_bottom)) +
		geom_point(size=2.5, aes(alpha=.5)) +
		guides(alpha=FALSE,color=FALSE, shape=FALSE) +
		theme(text=element_text(size=20)) + 
	    ggtitle('N bottom gaze points vs. fps (trial level)') + 
		theme(plot.title = element_text(size = 15, face = "bold"))

# Subject level
grouped = data_et %>%
	mutate(look_top = factor(
		as.numeric(y > 0.5))) %>%
	group_by(run_id, look_top) %>%
	dplyr::summarise(
		n = n(),
		.groups = 'keep') %>%
	merge(
		data_subject %>% dplyr::select(run_id, fps),
		by=c('run_id')) %>% 
	filter(!is.na(fps) & !is.na(n))

cor.test(grouped_bottom$n_bottom, grouped_bottom$fps) 

ggplot(grouped, 
       aes(x=fps, y=n, color=look_top)) +
	geom_point(size=2.5) +
	theme(text=element_text(size=20)) + 
    ggtitle('N gaze points vs. fps (subject level)') + 
		theme(plot.title = element_text(size = 15, face = "bold"))

## Filter high fps
fps_threshold = 15

runs_high_fps = data_subject %>%
	filter(fps >= fps_threshold) %>%
	dplyr::pull(run_id)
cat(paste('runs with fps >=', fps_threshold, ':', length(runs_high_fps)))

plot_et_time_bins(data_time_bins %>% filter(run_id %in% runs_high_fps))
ggsave(file.path(path_results, 'et', 'time_bins', 'fps_high.png'), 
			 width=5.5, height=5)

runs_low_fps = data_subject %>%
	filter(fps < fps_threshold) %>%
	dplyr::pull(run_id)
cat(paste('runs with fps <', fps_threshold, ':', length(runs_low_fps)))

plot_et_time_bins(data_time_bins %>% filter(run_id %in% runs_low_fps))
ggsave(file.path(path_results, 'et', 'time_bins', 'fps_low.png'), 
			 width=5.5, height=5)
```






### Data quality
```{r}
ggplot(data_subject, aes(offset))+
    geom_histogram(binwidth=0.025, alpha=.5, position="identity")+
    scale_fill_manual(values=c("palegreen","cornflowerblue"), name="") +
    theme_bw()+theme(text=element_text(size=40))

ggplot(data_subject, aes(precision))+
    geom_histogram(binwidth=0.01, alpha=.5, position="identity")+
    scale_fill_manual(values=c("palegreen","cornflowerblue"), name="") +
    theme_bw()+theme(text=element_text(size=40))

ggplot(data_subject, aes(fps))+
    geom_histogram(binwidth=1, alpha=.5, position="identity")+
    scale_fill_manual(values=c("palegreen","cornflowerblue"), name="") +
    theme_bw()+theme(text=element_text(size=40))


runs_plot = data_subject %>% 
	filter(
		offset <= 0.15 & 
		precision <= 0.06) %>%
	dplyr::pull(run_id)

print(paste('N runs:', length(runs_plot)))

plot_et_time_bins(data_time_bins %>% filter(run_id %in% runs_plot))
ggsave(file.path(path_results, 'et', 'time_bins', 'spatial_high.png'), 
			 width=5.5, height=5)

runs_plot = data_subject %>% 
	filter(
		offset > 0.15 & 
		precision > 0.06) %>%
	dplyr::pull(run_id)

print(paste('N runs:', length(runs_plot)))

plot_et_time_bins(data_time_bins %>% filter(run_id %in% runs_plot))
ggsave(file.path(path_results, 'et', 'time_bins', 'spatial_low.png'), 
			 width=5.5, height=5)
```

### What if participants do not look at the top option
```{r}
# Pos. ~ looking top --> top - bottom
grouped_tb_index = data_et %>% group_by(run_id, trial_index) %>%
	dplyr::summarise(
		look_top = sum(aoi %in% c('TL', 'TR')),
		look_bottom = sum(aoi %in% c('BL', 'BR')),
		tb_index = (look_top-look_bottom) / (look_top+look_bottom),
		.groups='keep')

grouped_tb_index

data_trial = merge_by_index(data_trial, grouped_tb_index, 'tb_index')

ggplot(data_trial, aes(tb_index)) +
    geom_histogram(binwidth=.1, alpha=.5, position="identity") +
    scale_fill_manual(values=c("palegreen","cornflowerblue"), name="") +
    theme_bw() + 
    ggtitle('Histogram of top_bottom relation (trial level)') + 
	theme(plot.title = element_text(size = 15, face = "bold"))
ggsave(file.path(path_results, 'et', 'tb_index_histogram_trial.png'), 
			 width=5.5, height=5)

# Subject level
grouped_tb_index = data_trial %>%
	group_by(run_id) %>%
	dplyr::summarise(
		tb_index = mean(tb_index),
		.groups = 'keep')

data_subject = merge_by_subject(data_subject, grouped_tb_index, 'tb_index')

ggplot(data_subject, aes(tb_index))+
    geom_histogram(binwidth=.1, alpha=.5, position="identity")+
    scale_fill_manual(values=c("palegreen","cornflowerblue"), name="") +
    theme_bw() + 
    ggtitle('Histogram of top_bottom relation (subject level)') + 
	theme(plot.title = element_text(size = 15, face = "bold"))
ggsave(file.path(path_results, 'et', 'tb_index_histogram_participants.png'), 
			 width=5.5, height=5)
```

### Only those trials who look at both options
When filtering for top_bottom_index, I get a tendency towards the middle
```{r}
bins_cleaned_tb_index =  data_et %>%
	merge_by_index(data_trial, 'choseTop') %>%
	merge_by_index(data_trial, 'tb_index') %>%
    filter(
    	!is.na(aoi) & aoi!=0 &
	   	tb_index > -0.99 & tb_index < 0.99) %>%
    mutate(
        lookTop = as.numeric(aoi %in% c('TL', 'TR')), 
        lookBottom = as.numeric(aoi %in% c('BL', 'BR'))) %>%
    dplyr::group_by(run_id, choseTop, time_bin) %>%
    dplyr::summarise(
        n = n(),
        n_lookTop = sum(lookTop),
        n_lookBottom = sum(lookBottom),    
        p_lookTop = sum(lookTop)/n,
        p_lookBottom = sum(lookBottom)/n,
        .groups = 'keep') %>%
	mutate(
		choseTop = factor(choseTop, c('1', '0')), 
		time_bin = factor(time_bin))

# Clean trials
print(paste('excluded', 
			data_trial %>% 
				filter(tb_index %in% c(-1, 1)) %>% 
				nrow(),
			'trials with tb_index in c(-1, 1). ',
			data_trial %>% 
				filter(!tb_index %in% c(-1, 1)) %>% 
				nrow(),
			'remain. '))

plot_et_time_bins(bins_cleaned_tb_index)
ggsave(file.path(path_results, 'et', 'time_bins', 'balanced_tb_index_trials.png'), 
			 width=5.5, height=5)

# Clean runs
runs_balanced_tb = data_subject %>%
	filter(tb_index > -0.8 & tb_index < 0.8) %>%
	dplyr::pull(run_id)
print(paste('N runs: ', length(runs_balanced_tb)))

plot_et_time_bins(data_time_bins %>% filter(run_id %in% runs_balanced_tb))
ggsave(file.path(path_results, 'et', 'time_bins',
				 'balanced_tb_index_participants.png'), 
	   width=5.5, height=5)
```




### What about those participants who never look down?
Are they less likely to choose the bottom option? Those trials, who have almost all gaze points in the upper half of the screen, are like 50% for choosing the top option. Same way vice versa, those trials who have almost all gaze points in the lower half, only had a chance of 60% for choosing the bottom areas
```{r}
grouped_top_bottom = data_et %>% 
	merge_by_index(data_trial, 'choseTop') %>%
	group_by(run_id, trial_index) %>%
	dplyr::summarise(
		n_top = sum(y > 0.5),
		n_bottom = sum(y < 0.5),
		choseTop = choseTop, 
		.groups = 'keep') %>%
	distinct()

only_top_n = grouped_top_bottom %>%
	filter(n_top > 25 & n_bottom < 1) %>% 
	nrow()

only_top_mean_choseTop = grouped_top_bottom %>%
	filter(n_top > 25 & n_bottom < 1) %>%
	dplyr::pull(choseTop) %>%
	mean()

cat(paste(
	'Those trials, where participants had more than 25 gaze points',
	'on the top option and zero gaze points on the bottom, had a ',
	'probability of',
	round(only_top_mean_choseTop, 2),
	'(', only_top_n, ' trials)',
	'for choosing the top option.'))

only_bottom_n = grouped_top_bottom %>%
	filter(n_top < 1 & n_bottom > 25) %>% 
	nrow()

only_bottom_mean_choseTop = grouped_top_bottom %>%
	filter(n_top < 1 & n_bottom > 25) %>%
	dplyr::pull(choseTop) %>%
	mean()

cat(paste(
	'Those trials, where participants had more than 25 gaze points',
	'on the bottom option and zero gaze points on the top, had a ',
	'probability of',
	round(only_bottom_mean_choseTop, 2),
	'(', only_bottom_n, ' trials)',
	'for choosing the top option.'))

grouped = data_trial %>%
	filter(tb_index %in% c(-1, 1)) %>%
	group_by(tb_index, run_id) %>%
	dplyr::summarise(
		n_trials = n(), 
		choseTop = mean(key_press==38),
		choseLL = mean(choseLL),
		.groups = 'keep') %>% 
	group_by(tb_index) %>%
	dplyr::summarise(
		n_participants = n(),
		n_trials = sum(n_trials),
		top = mean(choseTop), 
		top_std = sd(choseTop),
		LL = mean(choseLL), 
		LL_std = sd(choseLL),
		.groups='keep')

grouped

write.csv(grouped, file.path('results', 'tables', 'choice_task', 'biased_gaze.csv'))
```





### Reaction time
What if participants do not take the time to look at options and consider alternatives. Let's only look at those with 
```{r}
bins_longer_rts =  data_et %>%
	merge_by_index(data_trial, 'choseTop') %>%
	merge_by_index(data_trial, 'trial_duration_exact') %>%
    filter(
    	!is.na(aoi) & aoi!=0 &
    	trial_duration_exact > 1000) %>%
    mutate(
        lookTop = as.numeric(aoi %in% c('TL', 'TR')), 
        lookBottom = as.numeric(aoi %in% c('BL', 'BR'))) %>%
    dplyr::group_by(run_id, choseTop, time_bin) %>%
    dplyr::summarise(
        n = n(),
        n_lookTop = sum(lookTop),
        n_lookBottom = sum(lookBottom),    
        p_lookTop = sum(lookTop)/n,
        p_lookBottom = sum(lookBottom)/n,
        .groups = 'keep') %>%
	mutate(
		choseTop = factor(choseTop, c('1', '0')), 
		time_bin = factor(time_bin))

print(paste('How much data?', 
			length(unique(bins_longer_rts$run_id)),
			'runs ,',
			nrow(bins_longer_rts),
			'trials'))

plot_et_time_bins(bins_longer_rts)
ggsave(file.path(path_results, 'et', 'time_bins', 'long_rt_trial.png'), 
	   width=5.5, height=5)
```

### Left vs. right time bins
```{r}
bins_left_vs_right = data_et %>%
	merge_by_index(data_trial, 'choseLL') %>%
	merge_by_index(data_trial, 'amountLeft') %>%
    filter(!is.na(aoi) & aoi!=0) %>%
    mutate(
        look_amount = as.numeric(
        	(amountLeft==1 & aoi %in% c('TL', 'BL')) |
        	(amountLeft==0 & aoi %in% c('TR', 'BR')))) %>%
    dplyr::group_by(run_id, choseLL, time_bin) %>%
    dplyr::summarise(
        n = n(),
        n_look_amount = sum(look_amount),  
        p_look_amount = sum(look_amount)/n,
        .groups = 'keep') %>%
	mutate(
		choseLL = factor(choseLL, c('1', '0')), 
		time_bin = factor(time_bin))

bins_left_vs_right

ggplot(bins_left_vs_right, 
		aes(x=factor(time_bin), y=p_look_amount, 
			fill=choseLL)) + 
	geom_violin(alpha=.7, size=0, position="dodge") +
	stat_summary(
		fun=mean, geom="point", 
		shape=45, size=10, position=position_dodge(.9), 
		aes(color=choseLL)) +
	scale_colour_manual( 
		values=c("1"="black", "0"="white"), name="", 
		labels=c("Chose LL", "Chose SS")) +
	scale_fill_grey(
		start=.3, end=.7, name="",
	  	labels=c("Chose LL", "Chose SS")) +
	xlab("Time bins") + ylab("Proportion looking Amount") +
	theme_bw() + 
	theme(text=element_text(size=20), legend.position="bottom")
ggsave(file.path(path_results, 'et', 'time_bins', 'left_vs_right.png'), 
	   width=5.5, height=5)
```

