---
title: 'Analyzing eye-tracking behavior vs. choices'
output:
  html_document:
    df_print: paged
---

# Setup
```{r, setup, message=FALSE, warning=FALSE}
root = "C:/Users/User/GitHub/WebET_Analysis"

path_results = file.path(root, 'results', 'plots', 'amasino', 'choice_task')
# Create directory for plots
dir.create(file.path(path_results, 'et', 'time_bins'),
		   showWarnings = FALSE)

knitr::opts_knit$set(root.dir = normalizePath(file.path('..', '..')))

knitr::opts_knit$get("root.dir")


source(file.path(root, 'utils', 'r', 'geom_split_violin.R'))
source(file.path(root, 'utils', 'r', 'merge_by_subject.R'))
source(file.path(root, 'utils', 'r', 'merge_mean_by_subject.R'))
source(file.path(root, 'utils', 'r', 'merge_by_index.R'))
source(file.path(root, 'utils', 'r', 'summarize_datasets.R'))
source(file.path(root, 'utils', 'r', 'get_packages.R'))
source(file.path(root, 'utils', 'r', 'remove_runs.R'))
source(file.path(root, 'utils', 'r', 'add_x_count.R'))
source(file.path(root, 'utils', 'r', 'add_new_aoi.R'))

get_packages(c(
	'plyr',
	'dplyr', 
	"effsize",
	'e1071',
	"ggplot2",
	"ggsignif",
	'knitrProgressBar',
	'lme4',
	'progress',
	'QuantPsyc',
	"RColorBrewer",
	'reshape2',
	'tidyr'))

print(getwd())
```



# Prep data 
## Load data
```{r, load_datasets}
data_subject = read.csv(
    file.path(root, 'data', 'amasino', 'cleaned', 'data_subject.csv'))

data_trial = read.csv(
    file.path(root, 'data', 'amasino', 'cleaned', 'data_trial.csv'))

data_et = read.csv(
    file.path(root, 'data', 'amasino', 'cleaned', 'data_et.csv'))

summarize_datasets(data_et, data_trial, data_subject)
```

## Check AOI (optionally new AOIs)
```{r}
data_et = add_new_aoi(data_et, 0.35, 0.35)

ggplot(data_et %>% head(5000) %>% filter(aoi != 0), aes(x=x, y=y)) +
    geom_point(size=2.5, aes(alpha=.5))+
    guides(alpha=FALSE,color=FALSE, shape=FALSE)+
    theme_bw() + 
    scale_colour_grey() + 
    theme(text=element_text(size=20)) +
	ylim(1, 0) + 
    xlab("x") + ylab("y") +
    ggtitle('aois') 
```


# Gaze points ~ choice
```{r}
grouped = data_et %>% 
	merge_by_index(data_trial, 'choseTop') %>%
	merge_by_index(data_trial, 'choseLL') %>%
	merge_by_index(data_trial, 'LL_top') %>%
	filter(!is.na(aoi) & !aoi %in% c(0, '0')) %>%
	dplyr::group_by(run_id, trial_index) %>%
	dplyr::summarise(
		n = n(),
		n_bottom = sum(aoi %in% c('BL', 'BR')), 
		p_look_bottom = n_bottom / n,
		choseTop = mean(choseTop), 
		n_SS = sum(
			(LL_top==1 & aoi %in% c('BL', 'BR')) |
			(LL_top==0 & aoi %in% c('TL', 'TR'))),	
		p_SS = n_SS / n,
		choseLL = mean(choseLL),
		.groups = 'keep') %>%
	dplyr::group_by(run_id) %>%
	dplyr::summarise(
		n_look_bottom = sum(n_bottom),
		p_look_bottom = mean(p_look_bottom),
		choseTop = mean(choseTop), 
		n_SS = mean(n_SS), 
		p_SS = mean(p_SS), 
		choseLL = mean(choseLL),
		.groups = 'keep')

# grouped = data_et %>% 
# 	merge_by_index(data_trial, 'choseTop') %>%
# 	merge_by_index(data_trial, 'choseLL') %>%
# 	merge_by_index(data_trial, 'LL_top') %>%
# 	filter(!is.na(aoi) & !aoi %in% c(0, '0')) %>%
# 	dplyr::group_by(run_id) %>%
# 	dplyr::summarise(
# 		n = n(),
# 		n_bottom = sum(aoi %in% c('BL', 'BR')), 
# 		p_look_bottom = n_bottom / n,
# 		choseTop = mean(choseTop), 
# 		n_SS = sum(
# 			(LL_top==1 & aoi %in% c('BL', 'BR')) |
# 			(LL_top==0 & aoi %in% c('TL', 'TR'))),	
# 		p_SS = n_SS / n, 
# 		choseLL = mean(choseLL),
# 		.groups = 'keep')

cor.test(grouped$p_look_bottom, grouped$choseTop) 
cor.test(grouped$p_SS, grouped$choseLL) 
```


# Last fixation
```{r}
add_last_gaze = function(data_trial, data_et) {
    data_et = data_et %>%
    	merge_by_index(data_trial, 'LL_top') %>%
    	merge_by_index(data_trial, 'amountLeft') 
    
    grouped_lastCoordinate = data_et %>%
    	filter(aoi != 0 & !is.na(aoi)) %>%
        dplyr::group_by(run_id, trial_index) %>%
    	arrange(run_id, trial_index) %>%  
		slice(n()) %>%
        mutate(
        	lastGazeTop = factor(as.numeric(
        			aoi %in% c('TL', 'TR')),
        	   	c('0', '1')),
        	lastGazeLL = factor(as.numeric(
		            (aoi %in% c('TL', 'TR') & LL_top==1) |
		            (aoi %in% c('BL', 'BR') & LL_top==0)), 
	        	c('1', '0')),
            lastGazeSS = factor(as.numeric(
		            (aoi %in% c('TL', 'TR') & LL_top==0) |
		            (aoi %in% c('BL', 'BR') & LL_top==1)), 
	        	c('1', '0')),
			lastGaze_amount = factor(as.numeric(
		            (aoi %in% c('TL', 'BL') & amountLeft==1) |
		            (aoi %in% c('TR', 'BR') & amountLeft==0)), 
	        	c('1', '0')))

    data_trial = merge_by_index(data_trial, grouped_lastCoordinate,
    							'lastGazeTop')
	data_trial = merge_by_index(data_trial, grouped_lastCoordinate,
								'lastGazeLL')
	data_trial = merge_by_index(data_trial, grouped_lastCoordinate,
								'lastGazeSS')
	data_trial = merge_by_index(data_trial, grouped_lastCoordinate,
								'lastGaze_amount')
    return(data_trial)
}

data_trial = add_last_gaze(data_trial, data_et)
data_trial %>% dplyr::select(choseLL, LL_top, choseTop, lastGazeLL, lastGazeSS)
```

## Plot Look top
```{r}
grouped_last_fix_top = data_trial %>%
    dplyr::group_by(run_id, lastGazeTop, withinTaskIndex) %>%
    dplyr::summarise(
    	choseTop=mean(choseTop),
    	choseLL=mean(choseLL),
    	.groups = 'keep') %>%
    dplyr::group_by(run_id, lastGazeTop) %>%
    dplyr::summarise(
        n_trials=n(),
    	choseTop=mean(choseTop),
        choseLL=mean(choseLL),
        .groups = 'keep') 

ggplot(grouped_last_fix_top, aes(x=lastGazeTop, y=choseTop)) +
    geom_violin(fill="gray", size=0) +
    stat_summary(fun=mean,geom="point",shape=45,size=10, color="white") +
    theme_bw() + 
	ylim(0, 1) + 
    ylab("Proportion top choices") +
    xlab("last Fixation on Top AOIs") + 
    theme(text=element_text(size=20))
```

## Plot Look LL
```{r}
grouped_last_fix_LL = data_trial %>%
    dplyr::group_by(run_id, lastGazeLL, withinTaskIndex) %>%
    dplyr::summarise(
    	choseTop=mean(choseTop),
    	choseLL=mean(choseLL),
    	.groups = 'keep') %>%
    dplyr::group_by(run_id, lastGazeLL) %>%
    dplyr::summarise(
        n_trials=n(),
    	choseTop=mean(choseTop),
        choseLL=mean(choseLL),
        .groups = 'keep')

grouped_last_fix_LL %>%
	filter(lastGazeLL == 0)

ggplot(grouped_last_fix_LL, aes(x=lastGazeLL, y=choseLL)) +
    geom_violin(fill="gray", size=0) +
    stat_summary(fun=mean,geom="point",shape=45,size=10, color="white") +
    theme_bw() + 
    ylab("Proportion LL choices") +
    xlab("last Fixation on LL AOIs") + 
    theme(text=element_text(size=20))
```


## Plot Look SS
```{r}
grouped_last_fix_SS = data_trial %>%
	mutate(choseSS = as.numeric(choseLL==0)) %>%
    dplyr::group_by(run_id, lastGazeSS, withinTaskIndex) %>%
    dplyr::summarise(
    	choseTop=mean(choseTop),
    	choseSS=mean(choseSS),
    	.groups = 'keep') %>%
    dplyr::group_by(run_id, lastGazeSS) %>%
    dplyr::summarise(
        n_trials=n(),
    	choseTop=mean(choseTop),
        choseSS=mean(choseSS),
        .groups = 'keep')

grouped_last_fix_SS %>%
	filter(lastGazeSS == 0)

ggplot(grouped_last_fix_SS, aes(x=lastGazeSS, y=choseSS)) +
    geom_violin(fill="gray", size=0) +
    stat_summary(fun=mean,geom="point",shape=45,size=10, color="white") +
    theme_bw() + 
    ylab("Proportion SS choices") +
    xlab("last Fixation on SS AOIs") + 
    theme(text=element_text(size=20))
```


### Check on raw data
```{r}
data_et_raw = read.csv(
    file.path(root, 'data', 'amasino', 'raw', 'amasinoEtAl_ET_rep.csv'))
names(data_et_raw) = c('run_id', 'trial_index', 'x', 'y', 'fix_count')
data_trial_raw = read.csv(
    file.path(root, 'data', 'amasino', 'raw', 'amasinoEtAl_behavior.csv'))
names(data_trial_raw) = c('run_id', 'aSS', 'aLL', 'tSS', 'tLL', 
						  'choseLL', 'rt', 'LL_top', 'condition')

data_trial_raw$amountLeft = replace(
	data_trial_raw$LL_top, c(1, 2, 3, 4), c(1, 1, 0, 0))
data_trial_raw$LL_top = replace(
	data_trial_raw$LL_top, c(1, 2, 3, 4), c(1, 0, 1, 0))

data_trial_raw$trial_index = 0 
for (run in unique(data_trial_raw$run_id)) {
    data_trial_raw = data_trial_raw %>% 
    	mutate(trial_index = replace(
    		trial_index, run_id == run, 
    		c(1:nrow(data_trial_raw %>% filter(run_id==run)))))
}

data_et_raw = data_et_raw %>%
	merge_by_index(data_trial_raw, 'choseLL') %>%
	merge_by_index(data_trial_raw, 'LL_top') %>%
	merge_by_index(data_trial_raw, 'amountLeft')

data_et_raw$x = data_et_raw$x / 1280
data_et_raw$y = data_et_raw$y / 1024
data_et_raw = add_new_aoi(data_et_raw, 0.30, 0.30)

data_trial_raw = add_last_gaze(data_trial_raw, data_et_raw)

grouped_last_fix_LL = data_trial_raw %>%
    dplyr::group_by(run_id, lastGazeLL, trial_index) %>%
    dplyr::summarise(
    	choseLL=mean(choseLL),
    	.groups = 'keep') %>%
    dplyr::group_by(run_id, lastGazeLL) %>%
    dplyr::summarise(
        n_trials=n(),
        choseLL=mean(choseLL),
        .groups = 'keep')

ggplot(grouped_last_fix_LL, aes(x=lastGazeLL, y=choseLL)) +
    geom_violin(fill="gray", size=0) +
    stat_summary(fun=mean,geom="point",shape=45,size=10, color="white") +
    theme_bw() + 
    ylab("Proportion LL choices") +
    xlab("last Fixation on LL AOIs") + 
    theme(text=element_text(size=20))
```

## Plot last Fix Amount 
```{r}
grouped_last_fix_amount = data_trial %>%
    dplyr::group_by(run_id, lastGaze_amount, withinTaskIndex) %>%
    dplyr::summarise(
    	choseTop=mean(choseTop),
    	choseLL=mean(choseLL),
    	.groups = 'keep') %>%
    dplyr::group_by(run_id, lastGaze_amount) %>%
    dplyr::summarise(
        n_trials=n(),
    	choseTop=mean(choseTop),
        choseLL=mean(choseLL),
        .groups = 'keep') 

ggplot(grouped_last_fix_amount, aes(x=factor(lastGaze_amount), y=choseLL)) +
    geom_violin(fill="gray", size=0) +
    stat_summary(fun=mean,geom="point",shape=45,size=10, color="white") +
    theme_bw() + 
    ylab("Proportion LL choices") +
    xlab("last Fixation on LL AOIs") + 
    theme(text=element_text(size=20))
```

# Time bins
## Create bin dataset
## Eyetracking data bins
```{r}
create_time_bins = function(data, nBins) {
    data$time_bin = 0
    
    progress_bar <- progress_estimated(length(unique(data$run_id)), 0)
    
    for (subject in unique(data$run_id)){
    
        df_subject = data %>% filter(run_id == subject)
        
        for (trial in unique(df_subject$withinTaskIndex)) {
            df_trial = df_subject %>% filter(withinTaskIndex == trial)
            
            this_et_bin = cut(
                c(1:nrow(df_trial)), 
                nBins,
                labels = c(1:nBins),
                include.lowest=TRUE)
            
            data = data %>%
                mutate(time_bin=replace(
                    time_bin, 
                    run_id==subject & withinTaskIndex==trial, 
                    this_et_bin))
        }
        
        progress_bar$pause(0.1)$tick()$print()
        
    }
    return(data)
}

data_et = create_time_bins(data_et, 5)

data_time_bins =  data_et %>%
	merge_by_index(data_trial, 'choseTop') %>%
    filter(!is.na(aoi) & aoi!=0) %>%
    mutate(
        lookTop = as.numeric(aoi %in% c('TL', 'TR')), 
        lookBottom = as.numeric(aoi %in% c('BL', 'BR'))) %>%
    dplyr::group_by(run_id, choseTop, time_bin) %>%
    dplyr::summarise(
        n_trials = n(),
        n_lookTop = sum(lookTop),
        n_lookBottom = sum(lookBottom),    
        p_lookTop = sum(lookTop)/n_trials,
        p_lookBottom = sum(lookBottom)/n_trials,
        .groups = 'keep') %>%
	mutate(
		choseTop = factor(choseTop, c('1', '0')), 
		time_bin = factor(time_bin)) %>%
	dplyr::select(
		run_id, choseTop, time_bin, n_trials, 
		n_lookTop, n_lookBottom, p_lookTop, p_lookBottom)

data_time_bins
```



## Plot function
```{r}
plot_et_time_bins = function(data_time_bins) {

	runs_not_enough_bins = data_time_bins %>%
	    group_by(run_id, choseTop) %>%
	    dplyr::summarise(
	    	n=length(unique(time_bin)),
	    	.groups = 'keep') %>%
	    filter(n<5) %>%
	    dplyr::pull(run_id)
	
	print('These runs have less than 5 time bins: ')
	print(runs_not_enough_bins)
	
	bin_plot = ggplot(data_time_bins, 
		aes(x=factor(time_bin), y=p_lookTop, 
			fill=factor(choseTop, c('1', '0')))) + 
	geom_violin(alpha=.7, size=0, position="dodge") +
	stat_summary(
		fun=mean, geom="point", 
		shape=45, size=10, position=position_dodge(.9), 
		aes(color=factor(choseTop, c('1', '0')))) +
	scale_colour_manual( 
		values=c("1"="black", "0"="white"), name="", 
		labels=c("Chose top", "Chose bottom")) +
	scale_fill_grey(
		start=.3, end=.7, name="",
	  	labels=c("Chose top", "Chose bottom")) +
	xlab("Time bins") + ylab("Proportion looking top") +
	theme_bw() + 
	theme(text=element_text(size=20), legend.position="bottom")
	
	# Violin Plot
	# bin_plot = ggplot(data_time_bins, 
	#        aes(x=factor(time_bin), y=p_lookTop, fill=choseTop)) +
	#     geom_split_violin(alpha=0.7, size=1, position="dodge") +
	#     stat_summary(
	#         fun=mean, geom="point",
	#         shape=45,size=10,
	#         position=position_dodge(.9), 
	#         aes(color=factor(choseTop, c('1', '0')))) +
	#     theme_bw() + 
	#     theme(text=element_text(size=20), 
	#     legend.position="bottom") +
	#     ggtitle('Eye-tracking time bins') +
	#     scale_colour_manual(
	#         values=c("1"="black", "0"="white"), 
	#         name="", 
	#         labels=c("Chose Top", "Chose Bottom")) +
	#     scale_fill_grey(
	#         start=.3, end=.7, name="",
	#         labels=c("Chose Top", "Chose Bottom")) +
	#     ylab("Proportion looking top") +
	#     xlab("Time bins")
	
	print(bin_plot)
}
```

## All data
```{r}
plot_et_time_bins(data_time_bins)
```


## What if participants do not look at the top option
```{r}
# Pos. ~ looking top --> top - bottom
grouped_tb_index = data_et %>% group_by(run_id, trial_index) %>%
	dplyr::summarise(
		look_top = sum(aoi %in% c('TL', 'TR')),
		look_bottom = sum(aoi %in% c('BL', 'BR')),
		tb_index = (look_top-look_bottom) / (look_top+look_bottom),
		.groups='keep')

grouped_tb_index

data_trial = merge_by_index(data_trial, grouped_tb_index, 'tb_index')

ggplot(data_trial, aes(tb_index)) +
    geom_histogram(binwidth=.1, alpha=.5, position="identity") +
    scale_fill_manual(values=c("palegreen","cornflowerblue"), name="") +
    theme_bw() + 
    ggtitle('Histogram of top_bottom relation (trial level)') + 
	theme(plot.title = element_text(size = 15, face = "bold"))

# Subject level
grouped_tb_index = data_trial %>%
	group_by(run_id) %>%
	dplyr::summarise(
		tb_index = mean(tb_index),
		.groups = 'keep')

data_subject = merge_mean_by_subject(data_subject, grouped_tb_index, 'tb_index')

ggplot(data_subject, aes(tb_index))+
    geom_histogram(binwidth=.1, alpha=.5, position="identity")+
    scale_fill_manual(values=c("palegreen","cornflowerblue"), name="") +
    theme_bw() + 
    ggtitle('Histogram of top_bottom relation (subject level)') + 
	theme(plot.title = element_text(size = 15, face = "bold"))
```

### Only those trials who look at both options
When filtering for top_bottom_index, I get a tendency towards the middle
```{r}
bins_cleaned_tb_index =  data_et %>%
	merge_by_index(data_trial, 'choseTop') %>%
	merge_by_index(data_trial, 'tb_index') %>%
    filter(
    	!is.na(aoi) & aoi!=0 &
	   	tb_index > -0.99 & tb_index < 0.99) %>%
    mutate(
        lookTop = as.numeric(aoi %in% c('TL', 'TR')), 
        lookBottom = as.numeric(aoi %in% c('BL', 'BR'))) %>%
    dplyr::group_by(run_id, choseTop, time_bin) %>%
    dplyr::summarise(
        n = n(),
        n_lookTop = sum(lookTop),
        n_lookBottom = sum(lookBottom),    
        p_lookTop = sum(lookTop)/n,
        p_lookBottom = sum(lookBottom)/n,
        .groups = 'keep') %>%
	mutate(
		choseTop = factor(choseTop, c('1', '0')), 
		time_bin = factor(time_bin))

print(paste(
	'excluded', 
	data_trial %>% 
		filter(tb_index %in% c(-1, 1)) %>% 
		nrow(),
	'trials with tb_index in c(-1, 1). ',
	data_trial %>% 
		filter(!tb_index %in% c(-1, 1)) %>% 
		nrow(),
	'remain. '))


plot_et_time_bins(bins_cleaned_tb_index)

# Clean runs
runs_balanced_tb = data_subject %>%
	filter(tb_index > -0.8 & tb_index < 0.8) %>%
	dplyr::pull(run_id)
print(paste('N runs: ', length(runs_balanced_tb)))

plot_et_time_bins(data_time_bins %>% filter(run_id %in% runs_balanced_tb))
```




### What about those participants who never look down?
Are they less likely to choose the bottom option? Those trials, who have almost all gaze points in the upper half of the screen, are like 50% for choosing the top option. Same way vice versa, those trials who have almost all gaze points in the lower half, only had a chance of 60% for choosing the bottom areas
```{r}
grouped_top_bottom = data_et %>% 
	merge_by_index(data_trial, 'choseTop') %>%
	group_by(run_id, trial_index) %>%
	dplyr::summarise(
		n_top = sum(y > 0.5),
		n_bottom = sum(y < 0.5),
		choseTop = choseTop, 
		.groups = 'keep') %>%
	distinct()

only_top_n = grouped_top_bottom %>%
	filter(n_top > 25 & n_bottom < 1) %>% 
	nrow()

only_top_mean_choseTop = grouped_top_bottom %>%
	filter(n_top > 25 & n_bottom < 1) %>%
	dplyr::pull(choseTop) %>%
	mean()

cat(paste(
		'Those trials, where participants had more than 25 gaze points',
		'on the top option and zero gaze points on the bottom, had a ',
		'probability of',
		round(only_top_mean_choseTop, 2),
		'(', only_top_n, ' trials)',
		'for choosing the top option.'))

only_bottom_n = grouped_top_bottom %>%
	filter(n_top < 1 & n_bottom > 25) %>% 
	nrow()

only_bottom_mean_choseTop = grouped_top_bottom %>%
	filter(n_top < 1 & n_bottom > 25) %>%
	dplyr::pull(choseTop) %>%
	mean()

cat(paste(
		'Those trials, where participants had more than 25 gaze points',
		'on the bottom option and zero gaze points on the top, had a ',
		'probability of',
		round(only_bottom_mean_choseTop, 2),
		'(', only_bottom_n, ' trials)',
		'for choosing the top option.'))

grouped = data_trial %>%
	filter(tb_index %in% c(-1, 1)) %>%
	group_by(tb_index, run_id) %>%
	dplyr::summarise(
		n_trials = n(), 
		choseTop = mean(choseTop),
		choseLL = mean(choseLL),
		.groups = 'keep') %>% 
	group_by(tb_index) %>%
	dplyr::summarise(
		n_participants = n(),
		n_trials = sum(n_trials),
		top = mean(choseTop), 
		top_std = sd(choseTop),
		LL = mean(choseLL), 
		LL_std = sd(choseLL),
		.groups='keep')

grouped
```

## Left vs. right time bins
```{r}
bins_left_vs_right = data_et %>%
	merge_by_index(data_trial, 'choseLL') %>%
	merge_by_index(data_trial, 'amountLeft') %>%
    filter(!is.na(aoi) & aoi!=0) %>%
    mutate(
        look_amount = as.numeric(
        	(amountLeft==1 & aoi %in% c('TL', 'BL')) |
        	(amountLeft==0 & aoi %in% c('TR', 'BR')))) %>%
    dplyr::group_by(run_id, choseLL, time_bin) %>%
    dplyr::summarise(
        n = n(),
        n_look_amount = sum(look_amount),  
        p_look_amount = sum(look_amount)/n,
        .groups = 'keep') %>%
	mutate(
		choseLL = factor(choseLL, c('1', '0')), 
		time_bin = factor(time_bin))

bins_left_vs_right

ggplot(bins_left_vs_right, 
		aes(x=factor(time_bin), y=p_look_amount, 
			fill=choseLL)) + 
	geom_violin(alpha=.7, size=0, position="dodge") +
	stat_summary(
		fun=mean, geom="point", 
		shape=45, size=10, position=position_dodge(.9), 
		aes(color=choseLL)) +
	scale_colour_manual( 
		values=c("1"="black", "0"="white"), name="", 
		labels=c("Chose LL", "Chose SS")) +
	scale_fill_grey(
		start=.3, end=.7, name="",
	  	labels=c("Chose LL", "Chose SS")) +
	xlab("Time bins") + ylab("Proportion looking Amount") +
	theme_bw() + 
	theme(text=element_text(size=20), legend.position="bottom")

```


